---
title: "Adaptive barriers"
author: "Martina"
date: "Created in March, 2023. Last update: `r format(Sys.Date(), '%a %d %b, %Y')`"
output:
  rmarkdown::html_vignette:
  rmarkdown::pdf_document:
vignette: >
  %\VignetteIndexEntry{A barrier model illustration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: INLAspacetime.bib
---

```{r setup, include = FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dev.args = list(type = "cairo-png"),
  fig.width = 10,
  fig.height = 7,
  dpi = 300,
  out.width = "99%",
  fig.align = "center"
)
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

In this tutorial we illustrate a new implementation of the model proposed in @bakka2019barrier. 
It consider the problem of modeling over a spatial domain accounting for physical barriers. 
The original implementation is illustrated in
[this tutorial](https://haakonbakkagit.github.io/btopic128.html).
The re-implementation consider a new (faster) computational method 
available in the **INLA** package. 
See details at the end of this vignette to update old
working code to use this new implementation.

# Introduction

Suppose that there is a phenomena that varies over a spatial domain. 
Models usually consider correlation between observations made. 
Considering a pair of observations, the correlation is usually specified as 
a function of the distance between the location sites
from where these observations were collected. 
If there is a barrier in the spatial domain, 
this correlation for a pair of observations taken from sites in different 
sides of the barrier shall consider the barrier. 
In resume, it should no longer be just a function of the distance.
Basically, the correlation between points 
in two different sides of the barrier should decay faster (than the usual) 
to zero and "does not cross the domain". 

In order to illustrate the problem, 
let us define a rectangle as our spatial domain: 
```{r domain}
rxy <- c(10, 6)
r <- mean(rxy)
bb <- rbind(
    c(0, 1)*rxy[1],
    c(0, 1)*rxy[2])
domain <- cbind(
    c(0, 1, 1, 0, 0) * rxy[1],
    c(0, 0, 1, 1, 0) * rxy[2])
``` 

We will now set the barrier as the two polygons defined as follows
```{r bdomain}
barrier1 <- cbind(
  cos(seq(0, 2*pi, length=50)) * 0.7 + 0.50 * rxy[1], 
  sin(seq(0, 2*pi, length=50)) * 1.0 + 0.75 * rxy[2])
barrier2 <- cbind(
  c(0.50, 1.50, 1.50, 0.50, 0.50) * rxy[1],
  c(0.33, 0.33, 0.40, 0.40, 0.33) * rxy[2])
```

We can visualize these polygons in order to make the problem clear:
```{r domainvis}
par(mar = c(2, 2, 0, 0), mgp = c(2, 0.5, 0), las=1)
plot(t(bb), bty="n", type = "n", asp = 1)
polygon(domain, col = rgb(0.5,0.7,1))
polygon(barrier1, col = rgb(0.3,0.2,0.1, 0.5))
polygon(barrier2, col = rgb(0.3,0.2,0.1, 0.5))
```

The problem is to model data in both sides of the barrier considering that the 
correlation between then should account for the barrier. 
The proposed method in @bakka2019barrier 
models the entire domain, including the barrier. 
To deal with the barrier, the correlation range is set to be reasonable shorter 
over the barrier domain than the one at the domain of interest. 
This idea is simple and does not add any parameter in the usual stationary model. 
Furthermore, it can be implemented with any inferential method.

In @bakka2019barrier, the proposed method consider the 
Stochastic Partial Differential Equations - SPDE 
approach proposed in @lindgren2011explicit.
The implementation illustrated in
[this tutorial](https://haakonbakkagit.github.io/btopic128.html) 
deals with a discretization of the domain. 
The discretization should be considered with some care.
The fraction fixed for the analysis interplay with the width of the barrier. 
One should choose a small enough fraction, 
see details in @bakka2019barrier.

We first load the packages that will be used in this tutorial.

```{r packages}
library(INLA)
library(INLAspacetime)
library(inlabru)
library(ggplot2)
library(patchwork)
```

```{r inlaversioncheck, echo = FALSE}
iV <- grep("^Version", readLines(system.file("DESCRIPTION", package = "INLA")), value = TRUE)
```

```{r lic, echo = FALSE}
inla.setOption(
    pardiso.license = "~/.pardiso.lic" 
)
```

# Model definition and discretization

Let us consider that there is an underlying 
random field over the specified domain. 
This random field will be discretized using the mesh
so that a precision matrix is defined for the
distribution at the mesh nodes.
We will define the barrier model as
proposed in @bakka2019barrier
which make use of a triangulation.

# Mesh and triangles

The solution consider a discretization of the spatial domain and 
the simplest one is using triangles.
Therefore we start with the following mesh made up of small triangles 
in the domain and bigger around it.
```{r mesh}
mesh <- inla.mesh.2d(
    loc.domain = domain, 
    max.edge = c(0.03, 0.1) * r,
    offset = c(0.1, 0.3) * r,
    cutoff = 0.01 * r)
mesh$n
```

The solution needs the triangles inside the barrier domain to be identified. 
We start computing the center of each mesh triangle with
```{r triCenters}
triCenters <-
        (mesh$loc[mesh$graph$tv[,1], ] +
        mesh$loc[mesh$graph$tv[,2], ] +
        mesh$loc[mesh$graph$tv[,3], ]) / 3
``` 

For each triangle center we check if it is inside or not of the barrier domain
and create a vector to identify to which domain is each triangle center inside
```{r ibarrier}
isInBarrier <- (splancs::inout(triCenters, barrier1)) |
  (splancs::inout(triCenters, barrier2))
``` 

We can visualize the mesh and color the triangle centers 
using the **ggplot** methods from the **inlabru** package
```{r vmesh}
library(inlabru)
ggplot() +
    gg(mesh) +
    geom_point(aes(
        x = triCenters[,1],
        y = triCenters[,2],
        color = isInBarrier)) 
```

Notice that the mesh goes beyond the domain area including a boundary extension.
Then we also had defined the barrier so that it is also defined in this boundary.
Therefore, when building the model over this discretization, the barrier will
be well defined and the behavior of the process will be as intended.

## Precision matrix 

The parameters in this model are the range and the marginal variance,
We also define the range parameter in the barrier so that the method works.
We consider the range for the barrier as a fraction of the range over the domain.
We just use half of the average rectangle edges as the range in the domain
and 10% of it in the barrier. 
```{r rfparams}
sigma <- 1
(ranges <- r * c(0.5, 0.05)) 
```

We will implement the model with the mesh previously defined.
This start with defining which triangles have centers in the barrier.
```{r triBarrier}
triBarrier <- which(isInBarrier) 
length(triBarrier)
```

Then we compute the Finite Element matrices needed for the
model discretization, as detailed in @bakka2019barrier.
```{r bfem}
inla.barrier.fem

```

We now build the precision matrix with

Q <- ACA from paper



Fit the model using generic......

# References



