---
output: html_document
editor_options: 
  chunk_output_type: inline
---

# Barrier Model, 2 barriers example {#bm_2barriers}

## Simulation and inference with the Barrier model

```{r dt2 chunk1 inla.barrier.fem.plus013, include=FALSE}
inla.barrier.fem.plus <- function (mesh, barrier.triangles) 
  {
  n <- length(barrier.triangles) #barrier triangles list
  t <- length(mesh$graph$tv[, 1])
  total_triangles <- unlist(barrier.triangles)
  Omega <- list()
  Omega$remaining <- setdiff(1:t, total_triangles)
  for (k in 1:n) {
    Omega[k+1] <- barrier.triangles[k] 
    names(Omega)[k+1] <- paste0("barrier.triangles.", k)
  }
  
    dt.fem.white <- function(mesh, subdomain) {
        Ck <- rep(0, mesh$n)
        for (t in subdomain) {
            px <- mesh$graph$tv[t, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            area <- abs(det(Ts)) * 0.5
            for (i in 1:3) {
                Ck[px[i]] <- Ck[px[i]] + area
            }
        }
        return(Ck)
    }
    dt.fem.identity <- function(mesh) {
        len <- length(mesh$graph$tv[, 1])
        index.i <- rep(0, len * 6)
        index.j <- rep(0, len * 6)
        #index.q <- rep(0, len * 6)
        Aij <- rep(0, len * 6)
        counter <- 1
        for (t in 1:len) {
            px <- mesh$graph$tv[t, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            twiceArea <- abs(det(Ts))
            for (i in 1:3) {
                index.i[counter] <- px[i]
                index.j[counter] <- px[i]
                #index.q[counter] <- px[i]
                Aij[counter] <- (twiceArea) * 1/12
                counter <- counter + 1
            }
            for (i in 1:2) {
                for (j in (i + 1):3) {
                  index.i[counter] <- px[i]
                  index.j[counter] <- px[j]
                  Aij[counter] <- (twiceArea) * 1/24
                  counter <- counter + 1
                  index.i[counter] <- px[j]
                  index.j[counter] <- px[i]
                  Aij[counter] <- (twiceArea) * 1/24
                  counter <- counter + 1
                }
            }
        }
        I <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
            dims = c(mesh$n, mesh$n), repr = "T")
        return(I)
    }
    dt.fem.laplace <- function(mesh, subdomain) {
        Nphix <- rbind(c(-1, -1), c(1, 0), c(0, 1))
        len <- length(subdomain)
        index.i <- rep(0, len * 9)
        index.j <- rep(0, len * 9)
        Aij <- rep(0, len * 9)
        counter <- 1
        for (tri in subdomain) {
            px <- mesh$graph$tv[tri, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            TTTinv <- solve(t(Ts) %*% Ts)
            area <- abs(det(Ts)) * 0.5
            for (k in 1:3) {
                for (m in 1:3) {
                  tmp <- (3 * m + k - 4) * length(subdomain)
                  index.i[(tmp + counter)] <- px[k]
                  index.j[(tmp + counter)] <- px[m]
                  Aij[(tmp + counter)] <- area * Nphix[k, c(1, 
                    2)] %*% TTTinv %*% as.matrix(Nphix[m, c(1, 
                    2)])
                }
            }
            counter <- counter + 1
        }
        Dk <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
            dims = c(mesh$n, mesh$n), repr = "T")
        return(Dk)
    }
    xi <- length(Omega)
        fem <- list()
        fem$I <- dt.fem.identity(mesh)
        fem$D <- list()
        fem$C <- list()
        for (k in 1:xi) {
            fem$D[[k]] <- dt.fem.laplace(mesh, Omega[[k]])
        }
        for (k in 1:xi) {
            fem$C[[k]] <- dt.fem.white(mesh, Omega[[k]])
        }
        fem$hdim <- xi
    
    return(fem)
}

inla.barrier.q <- function (fem, ranges, sigma = 1, envir = NULL) 
{
    if (is.null(ranges)) 
        stop("ranges cannot be NULL")
    if (any(is.na(ranges))) 
        stop("No range can be NA")
    xi <- length(ranges)
    if (xi != length(fem$D)) {
        print("inla.barrier.q has encountered an error. Will stop.")
        stop("Ranges do no correspond to fem")
    }
    if (any(ranges < 0.001)) {
        warning("This hyper parameter value may fail. A very small maximum edge length needed in the mesh.")
    }
    Cdiag <- ranges[1]^2 * fem$C[[1]]
    if (xi > 1) {
        for (k in 2:xi) {
            Cdiag <- Cdiag + ranges[k]^2 * fem$C[[k]]
        }
    }
    N <- length(Cdiag)
    Cinv <- sparseMatrix(i = 1:N, j = 1:N, x = 1/Cdiag, dims = c(N, 
        N), repr = "T")
    A <- fem$I
    for (k in 1:xi) {
        A <- A + (ranges[k]^2/8) * fem$D[[k]]
    }
    Q <- inla.as.sparse(t(A) %*% Cinv %*% A * (1/sigma^2)/pi * 
        2 * 3)
    if (is.environment(envir)) {
        if (!exists("cache.done", envir = envir)) {
            Qx.idx <- which(Q@i <= Q@j)
            assign("Qx.idx", Qx.idx, envir = envir)
            assign("cache.done", TRUE, envir = envir)
        }
        else {
            Qx.idx <- get("Qx.idx", envir = envir)
        }
        return(Q@x[Qx.idx])
    }
    else {
        return(Q)
    }
}

inla.barrier.pcmatern.plus <- function (mesh, fem, barrier.triangles, prior.range, prior.sigma, range.fraction = 0.2) 
{
    if (missing(prior.range)) {
        warning("Arbitrary prior values chosen automatically. This may suffice for a first attempt, \n            but should be changed in any serious analysis.")
        prior.range <- c(diff(range(mesh$loc[, 1]))/5, 0.5)
    }
    if (missing(prior.sigma)) {
        prior.sigma <- c(1, 0.5) 
    }
    stopifnot(inherits(mesh, "inla.mesh"))
    stopifnot(range.fraction > 1e-06)
#    if (requireNamespace("INLAspacetime")) {
#        warning("Using implementation from the `INLAspacetime` package")
#        return(INLAspacetime::barrierModel.define(mesh = mesh, 
#            barrier.triangles = barrier.triangles, prior.range = prior.range, 
#            prior.sigma = prior.sigma, range.fraction = range.fraction))
#    }
#    else {
#        warning(paste("Please install the `INLAspacetime` package\n", 
#            "which contains an implementation that runs faster!"))
#    }
    barrier.rgeneric.model <- function(cmd = c("graph", "Q", 
        "mu", "initial", "log.norm.const", "log.prior", "quit"), 
        theta = NULL) {
        envir = parent.env(environment())
        prior.sigma <- obj$prior.sigma
        prior.range <- obj$prior.range
        fem <- obj$fem
        inla.barrier.q <- obj$inla.barrier.q
        range.fraction <- obj$range.fraction
        initial <- function(theta) {
            initial.theta <- c()
            if (!is.na(prior.sigma[2])) {
                initial.theta <- c(0, initial.theta)
            }
            if (!is.na(prior.range[2])) {
                initial.theta <- c(initial.theta, 0)
            }
            return(initial.theta)
        }
        log.prior <- function(theta) {
            val <- 0
            if (!is.na(prior.sigma[2])) {
                lambda0 <- -log(prior.sigma[2])/prior.sigma[1]
                val <- val + log(lambda0) - lambda0 * exp(theta[1]) + 
                  theta[1]
                theta.ran <- theta[-1]
            }
            else {
                theta.ran <- theta
            }
            if (!is.na(prior.range[2])) {
                lambda1 <- -log(prior.range[2]) * prior.range[1]
                for (logrange in theta.ran) {
                  val <- val + log(lambda1) - lambda1 * exp(-logrange) + 
                    -logrange
                }
            }
            return(val)
        }
        Q <- function(theta) {
            theta.full <- theta
            if (is.na(prior.sigma[2])) {
                theta.full <- c(log(prior.sigma[1]), theta.full)
            }
            if (is.na(prior.range[2])) {
                theta.full <- c(theta.full, log(prior.range[1]))
            }
            stopifnot(length(theta.full) == 2)
            Q <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]), 
                envir = envir) #ENVIR MAKES IT WORK
            return(Q)
        }
        graph <- function(theta) {
            require(methods)
            ntheta <- 2
            theta.full <- (1:ntheta)/3.217233456
            G1 <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G1[G1 != 0] <- 1
            theta.full <- (1:ntheta)^2/12.1543534
            G2 <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G2[G2 != 0] <- 1
            return(G1 + G2)
        }
        mu <- function(theta) numeric(0)
        log.norm.const <- function(theta) numeric(0)
        quit <- function(theta) invisible()
        val <- do.call(match.arg(cmd), args = list(theta))
        return(val)
    }
#   barrier.triangles <- unique(barrier.triangles)
    obj <- list()
    obj$prior.sigma <- prior.sigma
    obj$prior.range <- prior.range
    obj$range.fraction <- range.fraction
    obj$inla.barrier.q <- inla.barrier.q
    obj$fem <- fem
    barrier.model <- inla.rgeneric.define(model = barrier.rgeneric.model, 
        optimize = TRUE, obj = obj)
    if (!is.na(prior.sigma[2]) && !is.na(prior.range[2])) {
    }
    else {
        warning("Not properly tested, let us know if you have problems.")
    }
    return(barrier.model)
}

# local.plot.field_ same as local.plot.field, but I can modify the color paltte.

library(wesanderson)
# inla.barrier.polygon(mesh_kmD, barrier.triangles = barrier)
# ~Documents/Research/BasicFunctions/TUTORIAL Simulation and Inference BM.Rmd
# from: https://haakonbakkagit.github.io/btopic103.html
local.plot.field_ = function(field, mesh, 
                             xlim, ylim, 
                             dims=c(300, 300), 
                             pal, ...){
  if (missing(xlim)) {
        xlim = c(2, 8)
  }
  if (missing(ylim)) {
        ylim = xlim
  }
  if (missing(pal)) {
    pal = viridis::plasma(17) #17 before
  }
  
  proj = inla.mesh.projector(mesh, xlim = xlim, 
                             ylim = ylim, dims=c(300, 300))
  # - Can project from the mesh onto a 300x300 grid 
  #   for plots
  field.proj = inla.mesh.project(proj, field)
  # - Do the projection
  image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
             xlim = xlim, ylim = ylim, col = pal, ...)  
  # - Use image.plot to get nice colors and legend
}
# - This is the appropriate length of the field variable
# print(mesh_kmD$n)

# pp has if(missing(xlim))...
local.plot.fieldpp = function(field, mesh, poly.water, xlim, ylim, zlim, 
                              dims=c(300, 300),...){
 # poly.water = km_sp4msh, it has to be the SpatialPolygon object used in inla.mesh.2d
 # Error when using the wrong mesh
 stopifnot(length(field) == mesh$n)
    
 # Choose plotting region to be the same as the study area polygon
 if (missing(xlim)) xlim = poly.water@bbox[1, ] 
 if (missing(ylim)) ylim = poly.water@bbox[2, ]
    
 # Project the mesh onto a 300x300 grid   
 proj = inla.mesh.projector(mesh, xlim = xlim,                              
                            ylim = ylim, dims=c(300, 300)) 
 # Do the projection 
 field.proj = inla.mesh.project(proj, field)
       
 # Plot it
 image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
               xlim = xlim, ylim = ylim, zlim = zlim, ...)  
  }

library(fields)
library(viridisLite)
library(RColorBrewer)

book.rMatern <- function(n, coords, sigma=1, range, kappa = sqrt(8*nu)/range, variance = sigma^2, nu=1) {
    m <- as.matrix(dist(coords))
    m <- exp((1-nu)*log(2) + nu*log(kappa*m)-
             lgamma(nu))*besselK(m*kappa, nu)
    diag(m) <- 1
    return(drop(crossprod(chol(variance*m),
                          matrix(rnorm(nrow(coords)*n), ncol=n))))
}

book.rspde <- function(coords, sigma=1, range, variance=sigma^2, alpha=2, kappa = sqrt(8*(alpha-1))/range, n=1, mesh, 
                  verbose=FALSE, seed, return.attributes=FALSE) {
    t0 <- Sys.time()
    theta <- c(-0.5*log(4*pi*variance*kappa^2), log(kappa))
    if (verbose) cat('theta =', theta, '\n')
    if (missing(mesh)) {
        mesh.pars <- c(0.5, 1, 0.1, 0.5, 1)*sqrt(alpha-ncol(coords)/2)/kappa 
        if (verbose) cat('mesh.pars =', mesh.pars, '\n')
        attributes <- list(
            mesh=inla.mesh.2d(
                coords[chull(coords), ], max.edge=mesh.pars[1:2], 
                cutoff=mesh.pars[3], offset=mesh.pars[4:5]))
        if (verbose) cat('n.mesh =', attributes$mesh$n, '\n')
    }
    else attributes <- list(mesh=mesh)
    attributes$spde <- inla.spde2.matern(attributes$mesh, alpha=alpha)
    attributes$Q <- inla.spde2.precision(attributes$spde, theta=theta)
    attributes$A <- inla.mesh.project(mesh=attributes$mesh, loc=coords)$A
    if (n==1) 
        result <- drop(attributes$A%*%inla.qsample(
            Q=attributes$Q,
            constr=attributes$spde$f$extraconstr))
    t1 <- Sys.time() 
    result <- inla.qsample(n, attributes$Q, 
                           seed=ifelse(missing(seed), 0, seed), 
                           constr=attributes$spde$f$extraconstr) 
    if (nrow(result)<nrow(attributes$A)) {
        result <- rbind(result, matrix(
            NA, nrow(attributes$A)-nrow(result), ncol(result)))
        dimnames(result)[[1]] <- paste('x', 1:nrow(result), sep='')
        for (j in 1:ncol(result)) 
            result[, j] <- drop(attributes$A%*%
                                result[1:ncol(attributes$A),j])
    }
    else {
        for (j in 1:ncol(result)) 
            result[1:nrow(attributes$A), j] <-
                drop(attributes$A%*%result[,j]) 
        result <- result[1:nrow(attributes$A), ]
    }
    t2 <- Sys.time()
    attributes$cpu <- c(prep=t1-t0, sample=t2-t1, total=t2-t0)
    if (return.attributes) 
        attributes(result) <- c(attributes(result), attributes)
    return(drop(result))
}

book.mesh.dual <- function(mesh) {
    if (mesh$manifold=='R2') {
        ce <- t(sapply(1:nrow(mesh$graph$tv), function(i)
            colMeans(mesh$loc[mesh$graph$tv[i, ], 1:2])))
        library(parallel)
        pls <- mclapply(1:mesh$n, function(i) {
            p <- unique(Reduce('rbind', lapply(1:3, function(k) {
                j <- which(mesh$graph$tv[,k]==i)
                if (length(j)>0) 
                    return(rbind(ce[j, , drop=FALSE],
                                 cbind(mesh$loc[mesh$graph$tv[j, k], 1] +
                                       mesh$loc[mesh$graph$tv[j, c(2:3,1)[k]], 1], 
                                       mesh$loc[mesh$graph$tv[j, k], 2] +
                                       mesh$loc[mesh$graph$tv[j, c(2:3,1)[k]], 2])/2))
                else return(ce[j, , drop=FALSE])
            })))
            j1 <- which(mesh$segm$bnd$idx[,1]==i)
            j2 <- which(mesh$segm$bnd$idx[,2]==i)
            if ((length(j1)>0) | (length(j2)>0)) {
                p <- unique(rbind(mesh$loc[i, 1:2], p,
                                  mesh$loc[mesh$segm$bnd$idx[j1, 1], 1:2]/2 +
                                  mesh$loc[mesh$segm$bnd$idx[j1, 2], 1:2]/2, 
                                  mesh$loc[mesh$segm$bnd$idx[j2, 1], 1:2]/2 +
                                  mesh$loc[mesh$segm$bnd$idx[j2, 2], 1:2]/2))
                yy <- p[,2]-mean(p[,2])/2-mesh$loc[i, 2]/2
                xx <- p[,1]-mean(p[,1])/2-mesh$loc[i, 1]/2
            }
            else {
                yy <- p[,2]-mesh$loc[i, 2]
                xx <- p[,1]-mesh$loc[i, 1]
            }
            Polygon(p[order(atan2(yy,xx)), ])
        })
        return(SpatialPolygons(lapply(1:mesh$n, function(i)
            Polygons(list(pls[[i]]), i))))
    }
    else stop("It only works for R2!")
}

genColor <- function(n, type=c('red', 'green', 'blue'), u=NULL) {
    cbp <- list(
        red = list(c(255, 254, 252, 252, 251, 239, 203, 165, 103), 
                   c(245, 224, 187, 146, 106, 59, 24, 15, 0), 
                   c(240, 210, 161, 114, 74, 44, 29, 21, 13)), 
        green = list(c(247, 229, 199, 161, 116, 65, 35, 0, 0), 
                     c(252, 245, 233, 217, 196, 171, 139, 109, 68), 
                     c(245, 224, 192, 155, 118, 93, 69, 44, 27)), 
        blue = list(c(247, 222, 198, 158, 107, 66, 33, 8, 8), 
                    c(251, 235, 219, 202, 174, 146, 113, 81, 48), 
                    c(255, 247, 239, 225, 214, 198, 181, 156, 107)))
    if (n<2) stop("Works for 'n>2'!")
    if (is.null(u))
        u <- 0:(n-1)/(n-1)
    u0 <- 0:8/8
    i <- findInterval(u, u0, TRUE)
    k <- pmatch(match.arg(type), c('red', 'green', 'blue'))
    w1 <- 8*(u0[i+1]-u)/255; w2 <- 8*(u-u0[i])/255
    rgb(cbp[[k]][[1]][i]*w1 + cbp[[k]][[1]][i+1]*w2, 
        cbp[[k]][[2]][i]*w1 + cbp[[k]][[2]][i+1]*w2, 
        cbp[[k]][[3]][i]*w1 + cbp[[k]][[3]][i+1]*w2)
}

plot.dgTMatrix <- function(x, y, ...) {
    cl <- match.call()
    if (is.null(cl$digits))
        digits <- 2
    z <- sort(unique(round(x@x, digits)))
    nz <- length(z)
    n1 <- sum(z<0)
    n2 <- sum(z>0)
    if (is.null(cl$colors)) 
        if (any(c(n1,n2)==0)) 
            colors <- gray(0.9*(1-(z-min(z))/diff(range(z))))
        else
            colors <- c(genColor(n1, 'red', z[z<0]/min(z)),
                        rep('white', nz-n1-n2),
                        genColor(n2, 'blue', z[z>0]/max(z)))
    z.breaks <- c(z[1]-diff(z[1:2])/2,
                  z[-nz]/2 + z[-1]/2,
                  z[nz]+diff(z[nz-1:0])/2)
    x@x <- round(x@x, digits)
    image(x, at=z.breaks, col.regions=colors, ...)
}

book.plot.field <- function(field, mesh, projector, xlim, ylim, 
			    dims=c(300,300), poly, asp = 1, 
			    axes = FALSE, xlab = '', ylab = '', 
			    col = book.color.c(), ...){
  ## you can supply field as a matrix vector or like a named list with 'x', 'y' and 'z' as for image
  ## when field is a vector, it will project it using projector, assuming projector will create a matrix 
  ## when mesh is supplied and projector not, projector will be created and used to project field
  if (missing(mesh)) {
    if (missing(projector)) {
      if (missing(xlim) | missing(ylim)) {
        image.plot(field, asp = asp, axes = axes, 
                   xlab = xlab, ylab = ylab, col = col, ...)
      } else {
        image.plot(field, xlim = xlim, ylim = ylim, asp = asp, 
                   axes = axes, xlab = xlab, ylab = ylab, col = col, ...)
      }
    } else {
      if (missing(xlim)) xlim <- range(projector$x)
      if (missing(ylim)) ylim <- range(projector$y)
      field.proj <- inla.mesh.project(projector, field)
      image.plot(x = projector$x, y = projector$y, z = field.proj, 
                 asp=asp, axes=axes, xlab = xlab, ylab = ylab, 
                 col=col, xlim=xlim, ylim=ylim, ...)
    }
  } else {
    if (missing(xlim)) xlim <- range(mesh$loc[,1])
    if (missing(ylim)) ylim <- range(mesh$loc[,2])
    projector <- inla.mesh.projector(mesh, xlim = xlim,
                                     ylim = ylim, dims=dims)
    field.proj <- inla.mesh.project(projector, field)
    image.plot(x = projector$x, y = projector$y, z = field.proj, 
               asp=asp, axes=axes, xlab = xlab, ylab = ylab, col=col, ...)
  }
  if (!missing(poly)) 
      plot(poly, add = TRUE, col = 'grey')
}

## Functions for barrier models

## Find the correlation of precision Q (defined on mesh) at location 
book.spatial.correlation <- function(Q, location, mesh) {
  ## The marginal standard deviations
  sd <- sqrt(diag(inla.qinv(Q)))

  ## Create a fake A matrix, to extract the closest mesh node index
  A.tmp <- inla.spde.make.A(mesh = mesh,
    loc = matrix(c(location[1], location[2]), 1, 2))
  id.node = which.max(A.tmp[1, ])

  ## Solve a matrix system to find just one column of the covariance matrix
  Inode <- rep(0, dim(Q)[1])
  Inode[id.node] <- 1
  covar.column <- solve(Q, Inode)
  corr <- drop(matrix(covar.column)) / (sd * sd[id.node])
  return(corr)
}

## Continuous and discrete colour scales for the book
# n=8; plot(1:n, col=brewer.pal(n = n, name = "Paired"))

# Continuous
book.color.c = function(n = 201) {
  return(viridis(n))
}

# Continuous (alternative)
book.color.c2 = function(n = 201) {
  return(magma(n))
}

# Discrete from a continuous
book.color.dc = function(n = 11) {
  return(viridis(n))
}

# Discrete (cannot be interpolated)
book.color.d = function(n=4) {
  return(brewer.pal(n = n, name = "Paired"))
}

```

```{r dt2 chunk2 setup, warning=FALSE, message=FALSE}
library(INLA)
library(fields)
library(rgdal)
library(viridisLite)
library(scales)
library(ggplot2)
library(sf); library(terra); library(sp)

set.seed(2303) #8 befor
set.inla.seed <- 2303
```

```{r dt2 chunk3}
smalldist = 0.5
# - the width of the opening in the barrier
width = 0.4
# - The width/thickness of the barrier

local.square.polygon = function(xlim, ylim){
# - output is a square
  xlim = range(xlim); ylim = range(ylim)
  corner1 = c(xlim[1], ylim[2])
  corner2 = c(xlim[2], ylim[1])
  poly = Polygon(rbind(corner1, c(corner1[1], corner2[2]), corner2, c(corner2[1], corner1[2]), corner1), hole = FALSE)
  return(SpatialPolygons(list(Polygons(list(poly), ID = runif(1)))))
}

poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon")
```

############ 

Let´s do with different transparencies first.

```{r dt2 chunk4 5}
## --------------------------------------------------------------------------------
max.edge.length = 0.4
# - The coarseness of the finite element approximation
# - Corresponds to grid-square width in discretisations
# - - Except that finite element approximations are better
# - Should be compared to size of study area
# - Should be less than a fourth of the estimated (posterior) 
#   spatial range
# - Up to 8x computational time when you halve this value

## --------------------------------------------------------------------------------
loc1 = matrix(c(0,0, 10,0, 0,10, 10,10), 4, 2, byrow = T)
# - This defines the extent of the interior part of the mesh
# - In an application, if you want the mesh to depend on your 
#   data locations, you may use those locations instead
seg = inla.sp2segment(poly.original)
# - Transforms a SpatialPolygon to an "inla polygon"
mesh_ = inla.mesh.2d(loc=loc1, interior = seg, 
                    max.e = max.edge.length, offset=1)
mesh <- mesh_
# - The INLA mesh constructor, used for any INLA-SPDE model
```

```{r dt2 chunk5 7}
## --------------------------------------------------------------------------------
tl = length(mesh$graph$tv[,1])
# - the number of triangles in the mesh
posTri = matrix(0, tl, 2)
for (t in 1:tl){
  temp = mesh$loc[mesh$graph$tv[t, ], ]
  posTri[t,] = colMeans(temp)[c(1,2)] 
}
posTri = SpatialPoints(posTri)
# - the positions of the triangle centres
```

```{r dt2 chunk6 8}
# BARRIER ORIGINAL
bar.original = over(poly.original, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar.original = unlist(bar.original)
poly.bar.orginal = inla.barrier.polygon(mesh, barrier.triangles = bar.original)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 1
bar1 = over(poly1, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar1 = unlist(bar1)
poly.bar1 = inla.barrier.polygon(mesh, barrier.triangles = bar1)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 2
bar2 = over(poly2, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar2 = unlist(bar2)
poly.bar2 = inla.barrier.polygon(mesh, barrier.triangles = bar2)

# PLOTS
crs_longlat <- CRS("+proj=longlat +datum=WGS84")
crs_km <- CRS("+proj=utm +zone=39 ellps=WGS84 +units=km")
mesh_$crs <- crs_km

poly.bar.orginal_ <- st_as_sf(poly.bar.orginal) 
st_crs(poly.bar.orginal_) <- crs_km

poly.bar1_ <- st_as_sf(poly.bar1) 
st_crs(poly.bar1_) <- crs_km

poly.bar2_ <- st_as_sf(poly.bar2) 
st_crs(poly.bar2_) <- crs_km

gg_mesh2b <- ggplot() +
  inlabru::gg(mesh_, crs = crs_km) +
  geom_sf(data = poly.bar.orginal_, col = 'red') 

gg_meshlb <- ggplot() +
  inlabru::gg(mesh_, crs = crs_km) +
  geom_sf(data = poly.bar1_, col = 'red') 

gg_meshrb <- ggplot() +
  inlabru::gg(mesh_, crs = crs_km) +
  geom_sf(data = poly.bar2_, col = 'red') 
```

```{r dt2 chunk7 9}
## --------------------------------------------------------------------------------
local.plot.field = function(field, ...){
  xlim = c(2, 8); ylim = xlim;
  proj = inla.mesh.projector(mesh, xlim = xlim, 
                             ylim = ylim, dims=c(300, 300))
  # - Can project from the mesh onto a 300x300 grid 
  #   for plots
  field.proj = inla.mesh.project(proj, field)
  # - Do the projection
  image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
             xlim = xlim, ylim = ylim, col = plasma(17), ...)  # change for next code
  # - Use image.plot to get nice colors and legend
}
print(mesh$n)
# - This is the appropriate length of the field variable
```

ADD range.fraction ACCORDINGLY

```{r dt2 chunk8 12 proof for latter fem.plus function}
# this is to test the inla.barrier.fem function.
r1 <- 1; r2 <- 0.5; r3 <- 0.5
ranges.3 <- c(r1, r2, r3)
mat.plus <-  inla.barrier.fem.plus(mesh, list(bar1, bar2))
mat.original <- inla.barrier.fem(mesh, bar.original)

A <- mat.plus$I - 1/8*(r1^2*mat.plus$D[[1]] + r2^2*mat.plus$D[[2]] +  r3^2*mat.plus$D[[3]])
A1 <- mat.original$I - 1/8*(r1^2*mat.original$D[[1]] + r2^2*mat.original$D[[2]])
sum(A - A1)
```

```{r dt2 chunk9 11_, warning=FALSE, message=FALSE}
# Remeber that we don't modify range directly but r/something.
# passing a list with barrier 1 and barrier 2 using pcmatern.plus. Here we're using the same range (range.fraction) for both
pcmatern.p3 <-  
  inla.barrier.pcmatern.plus(mesh,
                             fem = mat.plus,
                             barrier.triangles = list(bar1, bar2),
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = c(0.1, 0.1))
barrier.model.p3 <- pcmatern.p3

# passing only 1 barrier using pcmatern.plus. 
# this is for comparison with inla pcmatern function
pcmatern.p2 <-  
  inla.barrier.pcmatern.plus(mesh,
                             fem = mat.original,
                             barrier.triangles = bar.original,
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = 0.1)
barrier.model.p2 <- pcmatern.p2

# same as pcmatern.p2 for comparison of functions inla.barrier.pcmatern and .plus
pcmatern.o <-  
  inla.barrier.pcmatern(mesh,
                             barrier.triangles = bar.original,
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = 0.1)
barrier.model.o <- pcmatern.o
```

```{r dt2 chunk10}
# Now let's try with different range fractions in the same model
pcmatern.p3.2b <-  
  inla.barrier.pcmatern.plus(mesh,
                             fem = mat.plus,
                             barrier.triangles = list(bar1, bar2),
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = c(0.5, 0.1))
barrier.model.p3.2b <- pcmatern.p3.2b
```

#### we're alright until here

BARRIER MODEL ORIGINAL

```{r dt2 chunk11}
range <- 20
# - the spatial range parameter
barrier.model <- barrier.model.o 
Q.barrier <- inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
# - the precision matrix for fixed ranges
# - Q is a function of the hyperparameters theta = c( log(sigma), log(range1), log(range2),...)
u <- inla.qsample(n=1, Q=Q.barrier, seed = set.inla.seed)
u <- u[ ,1]
u.p1 <- u
# - access the first sample
```

SAME PLOTS JUST DECIDE WHICH ONE IS BETTER

```{r dt2 chunk12}
par(mfrow= c(2,2))
local.plot.field(u, main="The true (simulated) spatial field",
                 sub = "barrier.model.o, range.fraction = 0.1")
proj <- inla.mesh.projector(mesh, xlim = c(2, 8), ylim = c(2, 8), dims = c(300, 300)) 
book.plot.field(u, projector = proj)

local.plot.field(u, main="The true (simulated) spatial field",
                 sub = "barrier.model.o, range.fraction = 0.1")
plot(poly.bar.orginal, add=T, col='grey')
# - Overlay the barrier with add=T
local.plot.field(u, main="The true (simulated) spatial field",
                 sub = "barrier.model.o, range.fraction = 0.1")
plot(poly.bar.orginal, add=T)
```
EXACT SAME AS BEFORE we change the object range and seed to chose the best one

```{r dt2 chunk11}
local.plot.field(inla.qsample(n=1, 
                              Q=inla.rgeneric.q(barrier.model,"Q", theta = c(0, log(3))),
                              seed = 2303)[ ,1])
proj <- inla.mesh.projector(mesh, xlim = c(2, 8), ylim = c(2, 8), dims = c(300, 300)) 
book.plot.field(u, projector = proj)

```



CODE FOR PLOTS WITH DIFFERENT RANGES This are again the exact same plots but with different gray rectangles overlay.

```{r dt2 chunk13}
par(mfrow = c(2,2))
local.plot.field(u, main= "Overlay left/right barrier", 
                   sub = "plot(poly.bar1, add=T, col='grey')")
plot(poly.bar1, add=T, col='grey')

local.plot.field(u, sub="plot(poly.bar2, add=T, col=alpha('grey', 0.5))")
plot(poly.bar2, add=T, col=alpha('grey', 0.5))

### 1,2 plots
local.plot.field(u, main= "Overlay left/right barrier with different transparencies", 
                   sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.3))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.3))
# here transparency is not r directly, it's just the col=alpha('grey', 0.3)

local.plot.field(u, sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.1))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.1))
```

Now the trues spatial field with different ranges.

BARRIER MODEL WITH MY FUNCTIONS, all plots should be exactly the same

```{r dt2 chunk14}
range <- 20
# - the spatial range parameter
barrier.model <- barrier.model.p2
Q.barrier <- inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
# - the precision matrix for fixed ranges
# - Q is a function of the hyperparameters theta = c( log(sigma), log(range1), log(range2),...)
u <- inla.qsample(n=1, Q=Q.barrier, seed = set.inla.seed)
u.p2 <- u[ ,1]
# - access the first sample
```

```{r dt2 chunk15}
range <- 20
# - the spatial range parameter
barrier.model <- barrier.model.p3
Q.barrier <- inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
# - the precision matrix for fixed ranges
# - Q is a function of the hyperparameters theta = c( log(sigma), log(range1), log(range2),...)
u <- inla.qsample(n=1, Q=Q.barrier, seed = set.inla.seed)
u.p3 <- u[ ,1]
# - access the first sample
```

```{r dt2 chunk16}
par(mfrow = c(2,2))
local.plot.field(u.p1, main="The true (simulated) spatial field",
                 sub = "barrier.model.o, range.fraction = 0.1")
local.plot.field(u.p2, main="The true (simulated) spatial field",
                 sub = "barrier.model.p2, range.fraction = 0.1")
local.plot.field(u.p3, main="The true (simulated) spatial field",
                 sub = "barrier.model.p3, range.fraction = (0.1, 0.1)")
```

PERFECT!

```{r dt2 chunk17}
range <- 20
# - the spatial range parameter
barrier.model <- barrier.model.p3.2b
Q.barrier <- inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
# - the precision matrix for fixed ranges
# - Q is a function of the hyperparameters theta = c( log(sigma), log(range1), log(range2),...)
u <- inla.qsample(n=1, Q=Q.barrier, seed = set.inla.seed)
u.p3.2b <- u[ ,1]
```

```{r dt2 chunk18}
par(mfrow = c(1,2))
local.plot.field(u.p3.2b, main="The true spatial field",
                 sub = "barrier.model.p3.2b, range.fraction = c(0.5, 0.1)")
# - access the first sample
local.plot.field(u.p1, main="The true spatial field",
                 sub = "barrier.model.o, range.fraction = 0.1")
```

PERFECT!

Now let's do a lot of plots, same width different range fractions

```{r dt2 chunk19}
mydiff.r <- function(mesh, fem, barrier.triangles, 
                     prior.range = c(1.44, 0.5), prior.sigma = c(0.7, 0.5),
                     range.fraction,
                     range = 20,
                     set.inla.seed = set.inla.seed,
                     return.list = FALSE) {
  
  barrier.model <- inla.barrier.pcmatern.plus(mesh, fem, barrier.triangles, 
                                              prior.range, prior.sigma, 
                                              range.fraction)
  # range fraction has to have the same length has barrier triangles
  Q <- inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
  u <- suppressWarnings(inla.qsample(n=1, Q=Q, seed = set.inla.seed))
  u <- u[ ,1]
  local.plot.field(u, main="True spatial field",
                   sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"))
  if (return.list == TRUE) {
    return(list(barrier.model = barrier.model, Q = Q, sample = u))
  }
}
```

.gif in plots.r (diff_r20.gif) shows results

```{r dt2 chunk20}
## view animated image
img_animated
```

######## 


btopic 103, simulate the spatial locations and the data

I'm here

```{r dt2 chunk21}
local.square.polygon_T = function(xlim, ylim){
# - output is a square
  xlim = range(xlim); ylim = range(ylim)
  corner1 = c(xlim[1], ylim[2])
  corner2 = c(xlim[2], ylim[1])
  poly = Polygon(rbind(corner1, c(corner1[1], corner2[2]), corner2, c(corner2[1], corner1[2]), corner1), hole = TRUE)
  return(poly)
}

# change xlim, and make it a hole
poly1_h <- local.square.polygon_T(xlim=c(2, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
#poly1; poly1_h@coords
poly2_h <- local.square.polygon_T(xlim=c(5+smalldist/2, 8), 
                          ylim=5+width*c(-.5, .5))
#poly2; poly2_h@coords

loc1 <- matrix(c(2,2, 8,2, 8,8, 2,8), 4, 2, byrow = T)
# plot(loc1)
locp <- Polygon(loc1, hole = FALSE)
# plot(SpatialPolygons(list(Polygons(list(locp), '1'))))

poly.water <- SpatialPolygons(list(Polygons(list(locp, poly1_h, poly2_h), '0')))
# plot(poly.water)
poly.water_sf <- st_as_sf(poly.water)

set.seed(set.inla.seed)
loc.data <- spsample(poly.water, n = 100, type = "random")
loc.data_sf <- st_as_sf(loc.data)
loc.data <- loc.data@coords
```


```{r}
mesh_h <-inla.mesh.2d(boundary = poly.water_sf, 
             max.e = max.edge.length, offset=1)

mesh_hb <-inla.mesh.2d(boundary = poly.water_sf, 
             max.edge = c(0.1, 0.4), 
             cutoff = c(0.02),
             offset=1)
# plot(st_geometry(poly.water_sf))
ggplot(data = poly.water_sf) + 
  inlabru::gg(mesh_h) + #plot mesh_hb alternatively
  geom_sf(data = loc.data_sf,
          col='purple',size=1.7,alpha=0.5)  
```

```{r dt2 chunk22}
# THIS IS THE SAME FOR ALL
A.data <- inla.spde.make.A(mesh, loc.data)
# - the projector matrix required for any spatial model
# - this matrix can transform the field-defined-on-the-mesh 
#   to the field-defined-on-the-data-locations
c(dim(A.data), mesh$n, nrow(loc.data))
# [1]  100 2570 2570  100
# - shows that the dimensions are correct
```


Until here the simulation is equal for all barriers. I'm excluding barriers for all.

Let's start the sample with 2 barriers with equal range, i.e. Q from barrier.model.o
Most of the code is general as the locations are the same. 
u is different.


```{r dt2 chunk23}
# THIS CHANGES 
# we only redefine u for barrier.model.o 'cause we lost it
Q.barrier.o <- inla.rgeneric.q(barrier.model.o, "Q", theta = c(0, log(range)))
u <- inla.qsample(n = 1, Q = Q.barrier.o, seed = set.inla.seed)[, 1]

u.data <- A.data %*% u
# - project the field from the finite element  
#   representation to the data locations

# THIS IS THE SAME
# df is the dataframe used for modeling
df <- data.frame(loc.data)
names(df) <- c('locx', 'locy')
# Size of the spatial signal
sigma.u <- 1
# Size of the measurement noise
sigma.epsilon <- 0.2

# DIFFERENT 'CAUSE IT HAS u.data
df$y <- drop(sigma.u * u.data + sigma.epsilon * rnorm(nrow(df)))
summary(df)
```


```{r dt2 chunk24}
#stk for simulated data with barriers
stk <- inla.stack(data=list(y=df$y), 
                  A=list(A.data, 1),
                  effects=list(s=1:mesh$n, 
                               intercept=rep(1, nrow(df))), 
                  remove.unused = FALSE, 
                  tag='est')
# in case I want to go back to this stk without running everything again:
stk.sim.bm <- stk
stk <- stk.sim.bm
```

```{r dt2 chunk25}
formula.bm <- y ~ 0 + intercept + f(s, model = barrier.model.o)
# - The spatial model component is different from stationary
# - The rest of the model setup is the same as in the stationary case!
# - - e.g. the inla(...) call below is the same, 
#     only this formula is different

res.barrier.o <- inla(formula.bm, data = inla.stack.data(stk),
       control.predictor = list(A = inla.stack.A(stk)),
       family = 'gaussian',
       control.family = list(hyper = list(
         prec = list(prior = "pc.prec", fixed = FALSE, param = c(0.2,0.5)))),
       control.mode=list(restart=T, theta=c(3.2, 0.4, 1.6)))
summary(res.barrier.o)
```

```{r dt2 chunk26}
par(mfrow= c(2,2))
# local.plot.field
local.plot.field(res.barrier.o$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model",
                 sub = "barrier.model.o, range.fraction = 0.1")

# same but with book.plot.spatial
proj <- inla.mesh.projector(mesh, xlim = c(2, 8), ylim = c(2, 8), dims = c(300, 300)) 
book.plot.field(res.barrier.o$summary.random$s$mean, projector = proj)

# local.plot.field with gray barriers
local.plot.field(res.barrier.o$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model",
                 sub = "barrier.model.o, range.fraction = 0.1")
plot(poly.bar.orginal, add=T, col='grey')

# plocal.plot.field with barrier contour
local.plot.field(res.barrier.o$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model",
                 sub = "barrier.model.o, range.fraction = 0.1")
plot(poly.bar.orginal, add=T)
```


############################
Now let's do a lot of plots, same width different range fractions
For 1

```{r dt2 chunk27}
# we saved u from p3.2b
u.data <- A.data %*% u.p3.2b
df$y <- drop(sigma.u * u.data + sigma.epsilon * rnorm(nrow(df)))
summary(df)
```

```{r dt2 chunk28}
#stk for simulated data with barriers
stk <- inla.stack(data=list(y=df$y), 
                  A=list(A.data, 1),
                  effects=list(s=1:mesh$n, 
                               intercept=rep(1, nrow(df))), 
                  remove.unused = FALSE, 
                  tag='est')
# in case I want to go back to this stk without running everything again:
stk.sim.p3.2b <- stk
stk <- stk.sim.p3.2b
```

```{r dt2 chunk29}
formula.bm <- y ~ 0 + intercept + f(s, model = barrier.model.p3.2b)
# - The spatial model component is different from stationary
# - The rest of the model setup is the same as in the stationary case!
# - - e.g. the inla(...) call below is the same, 
#     only this formula is different

res.barrier.p3.2b <- inla(formula.bm, data = inla.stack.data(stk),
       control.predictor = list(A = inla.stack.A(stk)),
       family = 'gaussian',
       control.family = list(hyper = list(
         prec = list(prior = "pc.prec", fixed = FALSE, param = c(0.2,0.5)))),
       control.mode=list(restart=T, theta=c(3.2, 0.4, 1.6)))
summary(res.barrier.p3.2b)
```

```{r dt2 chunk30}
# plocal.plot.field with barrier contour
par(mfrow = c(2,2))
local.plot.field(res.barrier.o$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model",
                 sub = "barrier.model.o, range.fraction = 0.1")
plot(poly.bar.orginal, add=T)

local.plot.field(res.barrier.p3.2b$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model",
                 sub = "barrier.model.p3.2b, range.fraction = c(0.5, 0,1)")
plot(poly.bar.orginal, add=T)
```
LET'S TRY TO DO A FUNCTION LIKE LAST ONE

```{r dt2 chunk31}
my_diff.pos <- function(mesh, loc.data, Q, u,
         sigma.u = 1, sigma.epsilon = 0.2,
         range.fraction = c(0.1, 0.1),
         pos = res.barrier$summary.random$s$mean,
         return.list = FALSE) {
  
  A.data <- inla.spde.make.A(mesh, loc.data)
  #Q from mydiff.r function
  u.data <- A.data %*% u
  df <- data.frame(loc.data)
  names(df) <- c('locx', 'locy')

  df$y <- drop(sigma.u * u.data + sigma.epsilon * rnorm(nrow(df)))
  
  stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
  formula <- y ~ 0 + intercept + f(s, model = barrier.model)
  # - The spatial model component is different from stationary
  # - The rest of the model setup is the same as in the stationary case!
  # - - e.g. the inla(...) call below is the same, 
  #     only this formula is different
  
  res.barrier <- inla(formula, data = inla.stack.data(stk),
                        control.predictor = list(A = inla.stack.A(stk)),
                        family = 'gaussian',
                        control.family = list(hyper = list(
                          prec = list(prior = "pc.prec", fixed = FALSE, param = c(0.2,0.5)))),
                        control.mode=list(restart=T, theta=c(3.2, 0.4, 1.6)))
  
  local.plot.field(pos, 
                   main="Spatial posterior for Barrier model",
                   sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"))
  plot(poly.bar.orginal, add=T)
  
  if (return.list == TRUE) {
    return(list(pos = quote(pos), df = df, summ.df = summary(df), 
                res = res.barrier, summ.res = summary(res.barrier)))
  }
}

```

```{r dt2 chunk32}
data4pos <- mydiff.r(mesh, fem = mat.plus, 
                     barrier.triangles = list(bar1, bar2),
                     range.fraction = c(0.1, 0.1),
                     return.list = TRUE)
data4pos2 <- mydiff.r(mesh, fem = mat.plus, 
                     barrier.triangles = list(bar1, bar2),
                     range.fraction = c(0.1, 0.8),
                     return.list = TRUE)

#my_diff.pos(mesh, loc.data, data4pos[[2]], u = data4pos$sample)
#suppressWarnings(my_diff.pos(mesh, loc.data, 
#                             data4pos2[[2]],
#                             data4pos2$sample, 
#                             range.fraction = c(0.1, 0.8)))

# THIS DOESN'T WORK RIGHT AWAY 'CAUSE IT NEEDS barrier.model
# it needs barrier.model <- inla.barrier.pcmatern.plus

data4pos$barrier.model
```


```{r}
# this works obviously
Q <- data4pos
u <- data4pos$sample
sigma.u = 1; sigma.epsilon = 0.2; range.fraction = c(0.1, 0.1)
     
A.data <- inla.spde.make.A(mesh, loc.data)
u.data <- A.data %*% u
df <- data.frame(loc.data)
names(df) <- c('locx', 'locy')

df$y <- drop(sigma.u * u.data + sigma.epsilon * rnorm(nrow(df)))
  
stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
formula <- y ~ 0 + intercept + f(s, model = barrier.model)

  # - The spatial model component is different from stationary
  # - The rest of the model setup is the same as in the stationary case!
  # - - e.g. the inla(...) call below is the same, 
  #     only this formula is different
```


```{r}
fem = mat.plus
barrier.triangles = list(bar1, bar2) 
prior.range = c(1.44, 0.5)
range.fraction = c(0.1, 0.1)
prior.sigma = c(0.7, 0.5)
barrier.model <- inla.barrier.pcmatern.plus(mesh, fem, barrier.triangles, 
                                            prior.range, prior.sigma, 
                                            range.fraction)
```


```{r}
res.barrier <- inla(formula, data = inla.stack.data(stk),
                    control.predictor = list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                        prec = list(
                          prior = "pc.prec", 
                          fixed = FALSE, 
                          param = c(0.2,0.5))))
                    )

pos <- res.barrier$summary.random$s$mean

local.plot.field(pos, 
                   main="Spatial posterior for Barrier model",
                   sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")")) 
plot(poly.bar.orginal, add=T)
  
list(pos = quote(pos), df = df, summ.df = summary(df), 
                res = res.barrier, summ.res = summary(res.barrier))


```



######## end of simulated data

### STATIONARY COMPARISON

```{r dt2 chunk33}
model.stat <- inla.spde2.pcmatern(mesh, prior.range = c(1, 0.5), 
                                  prior.sigma = c(1, 0.5))
# - Set up the model component for the spatial SPDE model: 
#   Stationary Matern model
# - I assume you are somewhat familiar with this model

formula <- y ~ 0 + intercept + f(s, model=model.stat)
# - Remove the default intercept
# - - Having it in the stack instead improves the numerical 
#     accuracy of the INLA algorithm
# - Fixed effects + random effects

res.stationary <- inla(formula, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))

summary(res.stationary)
local.plot.field(res.stationary$summary.random$s$mean,
          main="Spatial estimate with the stationary model")
plot(poly.original, add=T)
```


