
# Simulation and inference with the Barrier model

```{r 1}
## ----setup, include=FALSE--------------------------------------------------------
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)


## ---- warning=FALSE, message=FALSE-----------------------------------------------
library(INLA)
library(fields)
library(rgdal)
library(viridisLite)

set.seed(2016)
set.inla.seed = 2016
```

width just like in the example from btopic103

```{r 2}
## --------------------------------------------------------------------------------
smalldist = 0.2
# - the width of the opening in the barrier
width = 0.5
# - The width/thickness of the barrier

local.square.polygon = function(xlim, ylim){
# - output is a square
  xlim = range(xlim); ylim = range(ylim)
  corner1 = c(xlim[1], ylim[2])
  corner2 = c(xlim[2], ylim[1])
  poly = Polygon(rbind(corner1, c(corner1[1], corner2[2]), corner2, c(corner2[1], corner1[2]), corner1), hole = FALSE)
  return(SpatialPolygons(list(Polygons(list(poly), ID = runif(1)))))
}

poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon")
```

Change ´width´

```{r 3}
# - the width of the opening in the barrier is the same as before.
# - The width/thickness of the barrier: 
width_0.1 = 0.1
width_0.2 = 0.2
width_0.5 = 0.5
width_0.7 = 0.7
width_0.9 = 0.9
width_1.0 = 1
width_0.3 = 0.3
width_2.0 = 2
width_3.0 = 3
```

```{r 4}
par(mfrow=c(2,2))
width <- width_0.1
poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon", sub = "width = 0.1")

width <- width_0.5
poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon", sub = "width = 0.5")

width <- width_1.0
poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon", sub = "width = 1.0")

width <- width_2.0
poly1 = local.square.polygon(xlim=c(-1, 5-smalldist/2), 
                          ylim=5+width*c(-.5, .5))
poly2 = local.square.polygon(xlim=c(5+smalldist/2, 11), 
                          ylim=5+width*c(-.5, .5))
poly.original = SpatialPolygons(c(poly1@polygons, poly2@polygons))

plot(poly.original, main="Barrier area polygon", sub = "width = 2.0")
```

Hold that thought...

Lets play with different transparencies first.

```{r 5}
## --------------------------------------------------------------------------------
max.edge.length = 0.4
# - The coarseness of the finite element approximation
# - Corresponds to grid-square width in discretisations
# - - Except that finite element approximations are better
# - Should be compared to size of study area
# - Should be less than a fourth of the estimated (posterior) 
#   spatial range
# - Up to 8x computational time when you halve this value

## --------------------------------------------------------------------------------
loc1 = matrix(c(0,0, 10,0, 0,10, 10,10), 4, 2, byrow = T)
# - This defines the extent of the interior part of the mesh
# - In an application, if you want the mesh to depend on your 
#   data locations, you may use those locations instead
seg = inla.sp2segment(poly.original)
# - Transforms a SpatialPolygon to an "inla polygon"
mesh_ = inla.mesh.2d(loc=loc1, interior = seg, 
                    max.e = max.edge.length, offset=1)
mesh <- mesh_
# - The INLA mesh constructor, used for any INLA-SPDE model
```

```{r 6}
# DON'T RUN
# if I run the following then I only get one rectangle as "islands"
seg = inla.sp2segment(poly1)
# - Transforms a SpatialPolygon to an "inla polygon"
mesh = inla.mesh.2d(loc=loc1, interior = seg, 
                    max.e = max.edge.length, offset=1)
```

```{r 7}
## --------------------------------------------------------------------------------
tl = length(mesh$graph$tv[,1])
# - the number of triangles in the mesh
posTri = matrix(0, tl, 2)
for (t in 1:tl){
  temp = mesh$loc[mesh$graph$tv[t, ], ]
  posTri[t,] = colMeans(temp)[c(1,2)] 
}
posTri = SpatialPoints(posTri)
# - the positions of the triangle centres
```


```{r 8}
# BARRIER ORIGINAL
bar.original = over(poly.original, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar.original = unlist(bar.original)
poly.bar.orginal = inla.barrier.polygon(mesh, barrier.triangles = bar.original)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original


## --------------------------------------------------------------------------------
plot(mesh, main="Mesh and Omega")
plot(poly.bar.orginal, add=T, col='lightblue')
plot(mesh, add=T)
points(loc1)

# BARRIER 1
bar1 = over(poly1, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar1 = unlist(bar1)
poly.bar1 = inla.barrier.polygon(mesh, barrier.triangles = bar1)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original


## --------------------------------------------------------------------------------
plot(mesh, main="Mesh and Omega")
plot(poly.bar1, add=T, col='lightblue')
plot(mesh, add=T)
points(loc1)

# BARRIER 2
bar2 = over(poly2, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar2 = unlist(bar2)
poly.bar2 = inla.barrier.polygon(mesh, barrier.triangles = bar2)

plot(mesh, main="Mesh and Omega")
plot(poly.bar2, add=T, col='lightblue')
plot(mesh, add=T)
points(loc1)
```

ggplot nice figure in "0Version_Adaptive barrier models.Rdm"

```{r 9}
## --------------------------------------------------------------------------------
local.plot.field = function(field, ...){
  xlim = c(2, 8); ylim = xlim;
  proj = inla.mesh.projector(mesh, xlim = xlim, 
                             ylim = ylim, dims=c(300, 300))
  # - Can project from the mesh onto a 300x300 grid 
  #   for plots
  field.proj = inla.mesh.project(proj, field)
  # - Do the projection
  image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
             xlim = xlim, ylim = ylim, col = plasma(17), ...)  
  # - Use image.plot to get nice colors and legend
}
print(mesh$n)
# - This is the appropriate length of the field variable
```
DONT'T RUN
```{r 10}
## --------------------------------------------------------------------------------
barrier.model = inla.barrier.pcmatern(mesh, 
                                      barrier.triangles = bar.original, 
                                      prior.range = c(1.44, 0.5), 
                                      prior.sigma = c(0.7, 0.5), 
                                      range.fraction = 0.1)
```

DONT'T RUN
```{r 10}
# - Set up the inla model, including the matrices for solving the SPDE
barrier.model.plus <-  inla.barrier.pcmatern.plus(mesh, 
                                                  barrier.triangles = list(bar1, bar2),
                                                  prior.range = c(1.44, 0.5), 
                                                  prior.sigma = c(0.7, 0.5), 
                                                  range.fraction = 0.1)
```

ADD range.fraction ACCORDINGLY

```{r 12 proof for latter fem.plus function}
# this is to test the inla.barrier.fem function.
mat.plus <-  inla.barrier.fem.plus(mesh, list(bar1, bar2))
mat.original <- inla.barrier.fem(mesh, bar.original)

A <- mat.plus$I - 1/8*(r1^2*mat.plus$D[[1]] + r2^2*mat.plus$D[[2]] +  r3^2*mat.plus$D[[3]])
A1 <- mat.original$I - 1/8*(r1^2*mat.original$D[[1]] + r2^2*mat.original$D[[2]])
sum(A - A1)
```

```{r 11}
r1 = 1; r2 = 0.5; r3 = 0.5
ranges.3 <- c(r1, r2, r3)
fem.p <- inla.barrier.fem.plus(mesh, list(bar1, bar2))
barrier.q.p <- inla.barrier.q(fem.p, ranges.3, sigma = 1)

mat.plus <-  inla.barrier.fem.plus(mesh, list(bar1, bar2))
mat.original <- inla.barrier.fem(mesh, bar.original)

pcmatern.p3 <-  
  inla.barrier.pcmatern.plus(mesh,
                             fem = mat.plus,
                             barrier.triangles = list(bar1, bar2),
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = c(0.1, 0.1))
barrier.model.p3 <- pcmatern.p3

pcmatern.p2 <-  
  inla.barrier.pcmatern.plus(mesh,
                             fem = mat.original,
                             barrier.triangles = bar.original,
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = 0.1)
barrier.model.p2 <- pcmatern.p2

pcmatern.o <-  
  inla.barrier.pcmatern(mesh,
                             barrier.triangles = bar.original,
                             prior.range = c(1.44, 0.5), 
                             prior.sigma = c(0.7, 0.5),
                             range.fraction = 0.1)
barrier.model.o <- pcmatern.o
```


```{r}
## --------------------------------------------------------------------------------
range <- 3
# - the spatial range parameter
Q = inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
# - the precision matrix for fixed ranges
# - Q is a function of the hyperparameters theta = c( log(sigma), log(range1), log(range2),...)
```


```{r}
## --------------------------------------------------------------------------------
u = inla.qsample(n=1, Q=Q, seed = set.inla.seed)
u = u[ ,1]
# - access the first sample
```


```{r}
pal <- wes_palette(21, name = "Zissou1", type = "continuous")
par(mfrow = c(2, 2))

### 1,2 plots
local.plot.field(u, main="The true (simulated) spatial field",
                 sub = "local.plot.field()")
local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  sub = "local.plot.field_(..., pal = wes_palette)")

### 1,2 plots
local.plot.field(u, main="Overlay the barrier with plot(..., add=T)", 
                 sub="plot(poly.bar.orginal, add=T, col='grey')")
plot(poly.bar.orginal, add=T, col='grey')
# - Overlay the barrier with add=T
local.plot.field(u, sub="plot(poly.bar.orginal, add=T)")
plot(poly.bar.orginal, add=T)

### 1,2 plots
local.plot.field(u, main= "Overlay left/right barrier", 
                   sub = "plot(poly.bar1, add=T, col='grey')")
plot(poly.bar1, add=T, col='grey')

local.plot.field(u, sub="plot(poly.bar2, add=T, col=alpha('grey', 0.5))")
plot(poly.bar2, add=T, col=alpha('grey', 0.5))

### 1,2 plots
local.plot.field(u, main= "Overlay left/right barrier with different transparencies", 
                   sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.3))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.3))
# here transparency is not r directly, it's just the col=alpha('grey', 0.3)

local.plot.field(u, sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.1))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.1))


```


```{r}
## --------------------------------------------------------------------------------
num.try = 500 
# - try to sample this number of data locations
loc.try = matrix(runif(num.try*2, min=2, max=8), 
                         num.try, 2)
# - locations sampled inside the barrier will be removed 
#   in a few lines
temp = SpatialPoints(loc.try)
loc.ok = is.na(over(temp, poly.bar.orginal))
# - only allow locations that are not inside the Barrier area
loc.data = loc.try[loc.ok, ]
A.data = inla.spde.make.A(mesh, loc.data)
# - the projector matrix required for any spatial model
# - this matrix can transform the field-defined-on-the-mesh 
#   to the field-defined-on-the-data-locations
c(dim(A.data), mesh$n, nrow(loc.data))
# - shows that the dimensions are correct
u.data = A.data %*% u
# - project the field from the finite element  
#   representation to the data locations
```


```{r}
## --------------------------------------------------------------------------------
df = data.frame(loc.data)
# - df is the dataframe used for modeling
names(df) = c('locx', 'locy')
sigma.u = 1
# - size of the random effect
# - feel free to change this value
sigma.epsilon = 0.2
# - size of the iid noise in the Gaussian likelihood
# - feel free to change this value
df$y = drop(sigma.u*u.data + sigma.epsilon*rnorm(nrow(df)))
# - sample observations with gaussian noise


## --------------------------------------------------------------------------------
summary(df)
```


```{r}
## --------------------------------------------------------------------------------
stk <- inla.stack(data=list(y=df$y), A=list(A.data, 1),
                  effects=list(s=1:mesh$n, 
                               intercept=rep(1, nrow(df))), 
                  remove.unused = FALSE, tag='est')
# - this is the common stack used in INLA SPDE models
# - see the SPDE-tutorial
# - - http://www.r-inla.org/examples/tutorials/spde-tutorial
```


```{r}
## --------------------------------------------------------------------------------
model.stat = inla.spde2.pcmatern(mesh, prior.range = c(1, 0.5), prior.sigma = c(1, 0.5))
# - Set up the model component for the spatial SPDE model: 
#   Stationary Matern model
# - I assume you are somewhat familiar with this model

formula <- y ~ 0 + intercept + f(s, model=model.stat)
# - Remove the default intercept
# - - Having it in the stack instead improves the numerical 
#     accuracy of the INLA algorithm
# - Fixed effects + random effects

res.stationary <- inla(formula, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5))))) #,
#            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
## --------------------------------------------------------------------------------
summary(res.stationary)
```

```{r}
## --------------------------------------------------------------------------------
local.plot.field(res.stationary$summary.random$s$mean,
          main="Spatial estimate with the stationary model")
# - plot the posterior spatial marginal means
# - we call this the spatial estimate, or the smoothed data
plot(poly.bar.orginal , add=T, col='grey')
# - Posterior spatial estimate using the stationary model
```
```{r}
u <- res.stationary$summary.random$s$mean
pal <- wes_palette(21, name = "Zissou1", type = "continuous")
par(mfrow = c(2, 2))

### 1,2 plots
local.plot.field(u, main="Spatial estimate with the stationary model")
local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  sub = "local.plot.field_(..., pal = wes_palette)")

### 1,2 plots
local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  main="Overlay the barrier with plot(..., add=T)", 
                  sub="plot(poly.bar.orginal, add=T, col='grey')")
plot(poly.bar.orginal, add=T, col='grey')
# - Overlay the barrier with add=T
local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  sub="plot(poly.bar.orginal, add=T)")
plot(poly.bar.orginal, add=T)

### 1,2 plots
local.plot.field_(field = u, mesh = mesh, pal = pal,  
                  main= "Overlay left/right barrier", 
                  sub = "plot(poly.bar1, add=T, col='grey')")
plot(poly.bar1, add=T, col='grey')

local.plot.field_(field = u, mesh = mesh, pal = pal,
                  sub="plot(poly.bar2, add=T, col=alpha('grey', 0.5))")
plot(poly.bar2, add=T, col=alpha('grey', 0.5))

### 1,2 plots
local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  main= "Overlay left/right barrier with different transparencies", 
                  sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.3))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.3))
# here transparency is not r directly, it's just the col=alpha('grey', 0.3)

local.plot.field_(field = u, mesh = mesh, pal = pal, 
                  sub = "plot(add=T); plot(add=T, col=alpha('grey', 0.1))")
plot(poly.bar1, add=T, col='grey')
plot(poly.bar2, add=T, col=alpha('grey', 0.1))
```

Barrier model
This is the same model as we used for simulating the data. Except that we have now “forgotten” the range $r_b$ in the barrier area. This range is never known, so it is unreasonable to use it for inference. However, using any small value for the range in the barrier region is OK, it does not need to be the “true value”. For more information about this, see appendix “Choosing barrier range” in (Bakka et al. 2016). The Barrier model is a special case of the Different.


```{r}
## --------------------------------------------------------------------------------
barrier.model <- barrier.model.p2
formula2 <- y ~ 0 + intercept + f(s, model=barrier.model)
# - The spatial model component is different from before
# - The rest of the model setup is the same as in the stationary case!
# - - e.g. the inla(...) call below is the same, 
#     only this formula is different

## --------------------------------------------------------------------------------
res.barrier.p2 = inla(formula2, data=inla.stack.data(stk),
       control.predictor=list(A = inla.stack.A(stk)),
       family = 'gaussian',
       control.family = list(hyper = list(prec = list(
             prior = "pc.prec", fixed = FALSE, 
             param = c(0.2,0.5))))) #,
#       control.mode=list(restart=T, theta=c(3.2, 0.4, 1.6)))
```


```{r}
barrier.model <- barrier.model.o
formula2 <- y ~ 0 + intercept + f(s, model=barrier.model)
# - The spatial model component is different from before
# - The rest of the model setup is the same as in the stationary case!
# - - e.g. the inla(...) call below is the same, 
#     only this formula is different

## --------------------------------------------------------------------------------
res.barrier.o = inla(formula2, data=inla.stack.data(stk),
       control.predictor=list(A = inla.stack.A(stk)),
       family = 'gaussian',
       control.family = list(hyper = list(prec = list(
             prior = "pc.prec", fixed = FALSE, 
             param = c(0.2,0.5))))) #,
```


```{r}
barrier.model <- barrier.model.p3
formula2 <- y ~ 0 + intercept + f(s, model=barrier.model)
# - The spatial model component is different from before
# - The rest of the model setup is the same as in the stationary case!
# - - e.g. the inla(...) call below is the same, 
#     only this formula is different

## --------------------------------------------------------------------------------
res.barrier.p3 = inla(formula2, data=inla.stack.data(stk),
       control.predictor=list(A = inla.stack.A(stk)),
       family = 'gaussian',
       control.family = list(hyper = list(prec = list(
             prior = "pc.prec", fixed = FALSE, 
             param = c(0.2,0.5))))) #,
#       control.mode=list(restart=T, theta=c(3.2, 0.4, 1.6)))
```
  
```{r pcmatern.plus fx}
inla.barrier.pcmatern.plus <- function (mesh, fem, barrier.triangles, prior.range, prior.sigma, range.fraction = 0.2) 
{
    if (missing(prior.range)) {
        warning("Arbitrary prior values chosen automatically. This may suffice for a first attempt, \n            but should be changed in any serious analysis.")
        prior.range <- c(diff(range(mesh$loc[, 1]))/5, 0.5)
    }
    if (missing(prior.sigma)) {
        prior.sigma <- c(1, 0.5) 
    }
    stopifnot(inherits(mesh, "inla.mesh"))
    stopifnot(range.fraction > 1e-06)
#    if (requireNamespace("INLAspacetime")) {
#        warning("Using implementation from the `INLAspacetime` package")
#        return(INLAspacetime::barrierModel.define(mesh = mesh, 
#            barrier.triangles = barrier.triangles, prior.range = prior.range, 
#            prior.sigma = prior.sigma, range.fraction = range.fraction))
#    }
#    else {
#        warning(paste("Please install the `INLAspacetime` package\n", 
#            "which contains an implementation that runs faster!"))
#    }
    barrier.rgeneric.model <- function(cmd = c("graph", "Q", 
        "mu", "initial", "log.norm.const", "log.prior", "quit"), 
        theta = NULL) {
        envir = parent.env(environment())
        prior.sigma <- obj$prior.sigma
        prior.range <- obj$prior.range
        fem <- obj$fem
        inla.barrier.q <- obj$inla.barrier.q
        range.fraction <- obj$range.fraction
        initial <- function(theta) {
            initial.theta <- c()
            if (!is.na(prior.sigma[2])) {
                initial.theta <- c(0, initial.theta)
            }
            if (!is.na(prior.range[2])) {
                initial.theta <- c(initial.theta, 0)
            }
            return(initial.theta)
        }
        log.prior <- function(theta) {
            val <- 0
            if (!is.na(prior.sigma[2])) {
                lambda0 <- -log(prior.sigma[2])/prior.sigma[1]
                val <- val + log(lambda0) - lambda0 * exp(theta[1]) + 
                  theta[1]
                theta.ran <- theta[-1]
            }
            else {
                theta.ran <- theta
            }
            if (!is.na(prior.range[2])) {
                lambda1 <- -log(prior.range[2]) * prior.range[1]
                for (logrange in theta.ran) {
                  val <- val + log(lambda1) - lambda1 * exp(-logrange) + 
                    -logrange
                }
            }
            return(val)
        }
        Q <- function(theta) {
            theta.full <- theta
            if (is.na(prior.sigma[2])) {
                theta.full <- c(log(prior.sigma[1]), theta.full)
            }
            if (is.na(prior.range[2])) {
                theta.full <- c(theta.full, log(prior.range[1]))
            }
            stopifnot(length(theta.full) == 2)
            Q <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]),
                envir = envir)
            return(Q)
        }
        graph <- function(theta) {
            require(methods)
            ntheta <- 2
            theta.full <- (1:ntheta)/3.217233456
            G1 <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G1[G1 != 0] <- 1
            theta.full <- (1:ntheta)^2/12.1543534
            G2 <- inla.barrier.q(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G2[G2 != 0] <- 1
            return(G1 + G2)
        }
        mu <- function(theta) numeric(0)
        log.norm.const <- function(theta) numeric(0)
        quit <- function(theta) invisible()
        val <- do.call(match.arg(cmd), args = list(theta))
        return(val)
    }
#   barrier.triangles <- unique(barrier.triangles)
    obj <- list()
    obj$prior.sigma <- prior.sigma
    obj$prior.range <- prior.range
    obj$range.fraction <- range.fraction
    obj$inla.barrier.q <- inla.barrier.q
    obj$fem <- fem
    barrier.model <- inla.rgeneric.define(model = barrier.rgeneric.model, 
        optimize = TRUE, obj = obj)
    if (!is.na(prior.sigma[2]) && !is.na(prior.range[2])) {
    }
    else {
        warning("Not properly tested, let us know if you have problems.")
    }
    return(barrier.model)
}

```

```{r}
## --------------------------------------------------------------------------------
summary(res.barrier)


## --------------------------------------------------------------------------------
local.plot.field(res.barrier$summary.random$s$mean, 
                 main="Spatial posterior for Barrier model")
# - plot the posterior spatial marginal means
# - we call this the spatial (smoothing) estimate
plot(poly.barrier, add=T, col='grey')
# - Posterior spatial estimate using the Barrier model


## --------------------------------------------------------------------------------
res.barrier$summary.hyperpar


## --------------------------------------------------------------------------------
tmp = inla.tmarginal(function(x) exp(x), res.barrier$marginals.hyperpar[[2]]) 
plot(tmp, type = "l", xlab = "sigma", ylab = "Density")
xvals = seq(0, 10, length.out=1000)
lambda = 0.99; lines(xvals, 3*exp(-lambda*xvals), lty='dashed')
abline(v=1, col="blue")


## --------------------------------------------------------------------------------
tmp = inla.tmarginal(function(x) exp(x), res.barrier$marginals.hyperpar[[3]]) 
plot(tmp, type = "l", xlab = "r", ylab = "Density")
xvals = seq(0, 10, length.out=1000)
lambda = 1.00; lines(xvals, 3*exp(-lambda*xvals), lty='dashed')
abline(v=range, col="blue")


```

# Visualising spatial prior models



























