Functions using barrier,

+ inla.barrier.polygon(): 
  - barrier.model = inla.barrier.pcmatern(mesh, barrier.triangles = barrier, prior.range = c(1.44, 0.5), prior.sigma = c(0.7, 0.5), range.fraction = 0.1)
  
+ inla.barrier.fem()
  
+ inla.barrier.q()
  
+ inla.barrier.pcmatern()

For correlation matrix Q,

+ Stationary: ´Q = inla.spde2.precision(spde, theta = c(log(6),log(3)))´
+ Barrier model: ´Q = inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(6)))´
+ inla.qsample(n=1, Q=Q, seed = set.inla.seed)

```{r inla.barrier.fem original}
inla.barrier.fem
# done inla.barrier.fem.rmd
```

```{r}
inla.barrier.q
# this rmd
```

```{r inla.barrier.pcmatern original}
inla.barrier.pcmatern
# next
```

```{r inla.rgeneric.q original}
inla.rgeneric.q
# next
```

INLA.BARRIER.FEM

```{r my fem fx: inla.barrier.fem.plus}
# same as inla.barrier.fem.1.6
# 1.2. version has some preamble... and follows Janet's draft.

inla.barrier.fem.plus <- function (mesh, barrier.triangles) 
  {
  n <- length(barrier.triangles) #barrier triangles list
  t <- length(mesh$graph$tv[, 1])
  total_triangles <- unlist(barrier.triangles)
  Omega <- list()
  Omega$remaining <- setdiff(1:t, total_triangles)
  for (k in 1:n) {
    Omega[k+1] <- barrier.triangles[k] 
    names(Omega)[k+1] <- paste0("barrier.triangles.", k)
  }
  
    dt.fem.white <- function(mesh, subdomain) {
        Ck <- rep(0, mesh$n)
        for (t in subdomain) {
            px <- mesh$graph$tv[t, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            area <- abs(det(Ts)) * 0.5
            for (i in 1:3) {
                Ck[px[i]] <- Ck[px[i]] + area
            }
        }
        return(Ck)
    }
    dt.fem.identity <- function(mesh) {
        len <- length(mesh$graph$tv[, 1])
        index.i <- rep(0, len * 6)
        index.j <- rep(0, len * 6)
        #index.q <- rep(0, len * 6)
        Aij <- rep(0, len * 6)
        counter <- 1
        for (t in 1:len) {
            px <- mesh$graph$tv[t, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            twiceArea <- abs(det(Ts))
            for (i in 1:3) {
                index.i[counter] <- px[i]
                index.j[counter] <- px[i]
                #index.q[counter] <- px[i]
                Aij[counter] <- (twiceArea) * 1/12
                counter <- counter + 1
            }
            for (i in 1:2) {
                for (j in (i + 1):3) {
                  index.i[counter] <- px[i]
                  index.j[counter] <- px[j]
                  Aij[counter] <- (twiceArea) * 1/24
                  counter <- counter + 1
                  index.i[counter] <- px[j]
                  index.j[counter] <- px[i]
                  Aij[counter] <- (twiceArea) * 1/24
                  counter <- counter + 1
                }
            }
        }
        I <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
            dims = c(mesh$n, mesh$n), repr = "T")
        return(I)
    }
    dt.fem.laplace <- function(mesh, subdomain) {
        Nphix <- rbind(c(-1, -1), c(1, 0), c(0, 1))
        len <- length(subdomain)
        index.i <- rep(0, len * 9)
        index.j <- rep(0, len * 9)
        Aij <- rep(0, len * 9)
        counter <- 1
        for (tri in subdomain) {
            px <- mesh$graph$tv[tri, ]
            temp <- mesh$loc[px, ]
            p1 <- t(t(temp[1, c(1, 2)]))
            p2 <- t(t(temp[2, c(1, 2)]))
            p3 <- t(t(temp[3, c(1, 2)]))
            Ts <- cbind(p2 - p1, p3 - p1)
            TTTinv <- solve(t(Ts) %*% Ts)
            area <- abs(det(Ts)) * 0.5
            for (k in 1:3) {
                for (m in 1:3) {
                  tmp <- (3 * m + k - 4) * length(subdomain)
                  index.i[(tmp + counter)] <- px[k]
                  index.j[(tmp + counter)] <- px[m]
                  Aij[(tmp + counter)] <- area * Nphix[k, c(1, 
                    2)] %*% TTTinv %*% as.matrix(Nphix[m, c(1, 
                    2)])
                }
            }
            counter <- counter + 1
        }
        Dk <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
            dims = c(mesh$n, mesh$n), repr = "T")
        return(Dk)
    }
    xi <- length(Omega)
        fem <- list()
        fem$I <- dt.fem.identity(mesh)
        fem$D <- list()
        fem$C <- list()
        for (k in 1:xi) {
            fem$D[[k]] <- dt.fem.laplace(mesh, Omega[[k]])
        }
        for (k in 1:xi) {
            fem$C[[k]] <- dt.fem.white(mesh, Omega[[k]])
        }
        fem$hdim <- xi
    
    return(fem)
}
```

```{r Janet's draft fem fx: inla.barrier.fem.draft}
inla.barrier.fem.draft <- function (mesh, barrier.triangles, Omega = NULL) 
{
  stopifnot(inherits(mesh, "inla.mesh"))
  if (missing(barrier.triangles) && is.null(Omega)) 
    stop("Input barrier triangles")
  if (missing(barrier.triangles)) {
  }
  else {
    #barrier.triangles <- unique(barrier.triangles) b
    num_bar <- length(barrier.triangles)
    
    #     for (jj in 1:num_bar){
    #        paste("barrier.triangles",jj, sep = '') <- unlist(barrier.triangles[jj])}
    #layer with lower prob
    t <- length(mesh$graph$tv[, 1])
    remaining <- setdiff(1:t, unlist(barrier.triangles)) 
    #if (!is.null(Omega)) 
    #           warning("Omega is replaced by barrier.triangles")
    #Omega:option for creating a set of permeable barriers
    #triangles separated in lists. Prev code (next), with only 2 obj.
    #Omega <- list(remaining, barrier.triangles) 
    Omega <- list(remaining, barrier.triangles) #option 1
    #option 1: list with 3 obj. Same barrier taken as 2 different ones.
    #option 2: list with 2 obj. Maybe lower and higher prob triangles can be contain in the same list?
  }
  
  dt.fem.white <- function(mesh, subdomain) {
    Ck <- rep(0, mesh$n)
    for (t in subdomain) {
      px <- mesh$graph$tv[t, ]
      temp <- mesh$loc[px, ]
      p1 <- t(t(temp[1, c(1, 2)]))
      p2 <- t(t(temp[2, c(1, 2)]))
      p3 <- t(t(temp[3, c(1, 2)]))
      Ts <- cbind(p2 - p1, p3 - p1)
      area <- abs(det(Ts)) * 0.5
      for (i in 1:3) {
        Ck[px[i]] <- Ck[px[i]] + area
      }
    }
    return(Ck)
  }
  dt.fem.identity <- function(mesh) {
    len <- length(mesh$graph$tv[, 1])
    index.i <- rep(0, len * 6)
    index.j <- rep(0, len * 6)
    #index.q <- rep(0, len * 6)
    Aij <- rep(0, len * 6)
    counter <- 1
    for (t in 1:len) {
      px <- mesh$graph$tv[t, ]
      temp <- mesh$loc[px, ]
      p1 <- t(t(temp[1, c(1, 2)]))
      p2 <- t(t(temp[2, c(1, 2)]))
      p3 <- t(t(temp[3, c(1, 2)]))
      Ts <- cbind(p2 - p1, p3 - p1)
      twiceArea <- abs(det(Ts))
      for (i in 1:3) {
        index.i[counter] <- px[i]
        index.j[counter] <- px[i]
        #index.q[counter] <- px[i]
        Aij[counter] <- (twiceArea) * 1/12
        counter <- counter + 1
      }
      for (i in 1:2) {
        for (j in (i + 1):3) {
          index.i[counter] <- px[i]
          index.j[counter] <- px[j]
          Aij[counter] <- (twiceArea) * 1/24
          counter <- counter + 1
          index.i[counter] <- px[j]
          index.j[counter] <- px[i]
          Aij[counter] <- (twiceArea) * 1/24
          counter <- counter + 1
        }
      }
    }
    I <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
                      dims = c(mesh$n, mesh$n), repr = "T")
    return(I)
  }
  dt.fem.laplace <- function(mesh, subdomain) {
    Nphix <- rbind(c(-1, -1), c(1, 0), c(0, 1))
    len <- length(subdomain)
    index.i <- rep(0, len * 9)
    index.j <- rep(0, len * 9)
    Aij <- rep(0, len * 9)
    counter <- 1
    for (tri in subdomain) {
      px <- mesh$graph$tv[tri, ]
      temp <- mesh$loc[px, ]
      p1 <- t(t(temp[1, c(1, 2)]))
      p2 <- t(t(temp[2, c(1, 2)]))
      p3 <- t(t(temp[3, c(1, 2)]))
      Ts <- cbind(p2 - p1, p3 - p1)
      TTTinv <- solve(t(Ts) %*% Ts)
      area <- abs(det(Ts)) * 0.5
      for (k in 1:3) {
        for (m in 1:3) {
          tmp <- (3 * m + k - 4) * length(subdomain)
          index.i[(tmp + counter)] <- px[k]
          index.j[(tmp + counter)] <- px[m]
          Aij[(tmp + counter)] <- area * Nphix[k, c(1, 
                                                    2)] %*% TTTinv %*% as.matrix(Nphix[m, c(1, 
                                                                                            2)])
        }
      }
      counter <- counter + 1
    }
    Dk <- sparseMatrix(i = index.i, j = index.j, x = Aij, 
                       dims = c(mesh$n, mesh$n), repr = "T")
    return(Dk)
  }
  xi <- num_bar
  fem <- list()
  fem$I <- dt.fem.identity(mesh)
  fem$D <- list()
  fem$C <- list()
  fem$D[[1]] <- dt.fem.laplace(mesh, Omega[[1]])
  fem$C[[1]] <- dt.fem.white(mesh, Omega[[1]])
  for (k in 1:xi) {
    fem$D[[k+1]] <- dt.fem.laplace(mesh, Omega[[2]][[k]])
  }
  for (k in 1:xi) {
    fem$C[[k+1]] <- dt.fem.white(mesh, Omega[[2]][[k]])
  }
  fem$hdim <- xi + 1
  
  return(fem)
}
```

```{r proof for latter fx}
##eq 8
##Draft function Janet August 20
mat <- inla.barrier.fem.draft(mesh, list(triBarrier1, triBarrier2))
mat1 <- inla.barrier.fem(mesh, triBarrier)
#Test
r1 = 1
r2 = 0.5
r3 = 0.5
A = mat$I - 1/8*(r1^2*mat$D[[1]] + r2^2*mat$D[[2]] +  r3^2*mat$D[[3]])
A1 = mat1$I - 1/8*(r1^2*mat1$D[[1]] + r2^2*mat1$D[[2]])

sum.draft <- sum(A - A1)

## Draft function if barrier is the same?
mat <- inla.barrier.fem.plus(mesh, list(triBarrier1, triBarrier2))
mat1 <- inla.barrier.fem(mesh, triBarrier)
#Test
A = mat$I - 1/8*(r1^2*mat$D[[1]] + r2^2*mat$D[[2]] +  r3^2*mat$D[[3]])
A1 = mat1$I - 1/8*(r1^2*mat1$D[[1]] + r2^2*mat1$D[[2]])

sum.plus <- sum(A - A1)
```


```{r proof for latter fx}
mat$D[[1]][1,1] == mat$D[[3]][1,1]
which(mat$D[[1]] != mat$D[[3]])
which(mat$D[[2]] != mat$D[[3]])
```

obj fem definitions for later

```{r obj fem definitions for later}
fem.original <- inla.barrier.fem(mesh, triBarrier)
fem <- inla.barrier.fem.plus(mesh, list(triBarrier1, triBarrier2))
length(fem$D)
str(fem);str(fem.original)
```

INLA.BARRIER.Q

```{r inla.barrier.q.plus}
inla.barrier.q.plus <- function (fem, ranges, sigma = 1) 
{
    if (is.null(ranges)) 
        stop("ranges cannot be NULL")
    if (any(is.na(ranges))) 
        stop("No range can be NA")
    xi <- length(ranges)
    if (xi != length(fem$D)) {
        print("inla.barrier.q has encountered an error. Will stop.")
        stop("Ranges do no correspond to fem")
    }
    if (any(ranges < 0.001)) {
        warning("This hyper parameter value may fail. A very small maximum edge length needed in the mesh.")
    }
    Cdiag <- ranges[1]^2 * fem$C[[1]]
    if (xi > 1) {
        for (k in 2:xi) {
            Cdiag <- Cdiag + ranges[k]^2 * fem$C[[k]] ##eq (9) 
        }
    }
    N <- length(Cdiag)
    Cinv <- sparseMatrix(i = 1:N, j = 1:N, x = 1/Cdiag, dims = c(N, 
        N), repr = "T")
    A <- fem$I
    for (k in 1:xi) {
        A <- A + (ranges[k]^2/8) * fem$D[[k]]
    }
    Q <- inla.as.sparse(t(A) %*% Cinv %*% A * (1/sigma^2)/pi * 
        2 * 3)
#    if (is.environment(envir)) {
#        if (!exists("cache.done", envir = envir)) {
#            Qx.idx <- which(Q@i <= Q@j)
#            assign("Qx.idx", Qx.idx, envir = envir)
#            assign("cache.done", TRUE, envir = envir)
#        }
#        else {
#            Qx.idx <- get("Qx.idx", envir = envir)
#        }
#        return(Q@x[Qx.idx])
#    }
#    else {
        return(Q)
#    }
  }

```

```{r random inside fx trials}
C1 <- ranges[1]^2 * fem$C[[1]]
head(Cdiag) #Cdiag from fx

Cdiag_ <- ranges[1]^2 * fem$C[[1]] + ranges[2]^2 * fem$C[[2]] + ranges[3]^2 * fem$C[[3]] ##eq (9) 
which(C1 != Cdiag_)
C1[which(C1 != Cdiag_)];Cdiag[which(C1 != Cdiag_)]
C1[c(110, 142)];Cdiag_[c(110, 142)]

which(Cdiag != Cdiag_) #is Cdiag from fx = to sum by hand Cdiag_?
```

obj q definitions for later

```{r test if inla.barrier.q works}
r1 = 1
r2 = 0.05
r3 = 0.1
fem.original <- inla.barrier.fem(mesh, triBarrier)
fem <- inla.barrier.fem.plus(mesh, list(triBarrier1, triBarrier2))
ranges.3 <- c(r1, r2, r3)
ranges.2 <- c(r1, r2)
q.plus <- inla.barrier.q.plus(fem, ranges.3, sigma = 1) 
q.original <- inla.barrier.q(fem.original, ranges.2)
str(q.original); str(q.plus)
which(q.original != q.plus)
```

INLA.BARRIER.PCMATERN

```{r inla.barrier.pcmatern.plus}
inla.barrier.pcmatern.plus <- function (mesh, barrier.triangles, prior.range, prior.sigma, 
    range.fraction = 0.2) 
{
    if (missing(prior.range)) {
        warning("Arbitrary prior values chosen automatically. This may suffice for a first attempt, \n            but should be changed in any serious analysis.")
        prior.range <- c(diff(range(mesh$loc[, 1]))/5, 0.5)
    }
    if (missing(prior.sigma)) {
        prior.sigma <- c(1, 0.5) 
    }
    stopifnot(inherits(mesh, "inla.mesh"))
    stopifnot(range.fraction > 1e-06)
#    if (requireNamespace("INLAspacetime")) {
#        warning("Using implementation from the `INLAspacetime` package")
#        return(INLAspacetime::barrierModel.define(mesh = mesh, 
#            barrier.triangles = barrier.triangles, prior.range = prior.range, 
#            prior.sigma = prior.sigma, range.fraction = range.fraction))
#    }
#    else {
#        warning(paste("Please install the `INLAspacetime` package\n", 
#            "which contains an implementation that runs faster!"))
#    }
    barrier.rgeneric.model <- function(cmd = c("graph", "Q", 
        "mu", "initial", "log.norm.const", "log.prior", "quit"), 
        theta = NULL) {
        envir = parent.env(environment())
        prior.sigma <- obj$prior.sigma
        prior.range <- obj$prior.range
        fem <- obj$fem
        inla.barrier.q <- obj$inla.barrier.q.plus
        range.fraction <- obj$range.fraction
        initial <- function(theta) {
            initial.theta <- c()
            if (!is.na(prior.sigma[2])) {
                initial.theta <- c(0, initial.theta)
            }
            if (!is.na(prior.range[2])) {
                initial.theta <- c(initial.theta, 0)
            }
            return(initial.theta)
        }
        log.prior <- function(theta) {
            val <- 0
            if (!is.na(prior.sigma[2])) {
                lambda0 <- -log(prior.sigma[2])/prior.sigma[1]
                val <- val + log(lambda0) - lambda0 * exp(theta[1]) + 
                  theta[1]
                theta.ran <- theta[-1]
            }
            else {
                theta.ran <- theta
            }
            if (!is.na(prior.range[2])) {
                lambda1 <- -log(prior.range[2]) * prior.range[1]
                for (logrange in theta.ran) {
                  val <- val + log(lambda1) - lambda1 * exp(-logrange) + 
                    -logrange
                }
            }
            return(val)
        }
        Q <- function(theta) {
            theta.full <- theta
            if (is.na(prior.sigma[2])) {
                theta.full <- c(log(prior.sigma[1]), theta.full)
            }
            if (is.na(prior.range[2])) {
                theta.full <- c(theta.full, log(prior.range[1]))
            }
            stopifnot(length(theta.full) == 2)
            Q <- inla.barrier.q.plus(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]), 
                envir = envir)
            return(Q)
        }
        graph <- function(theta) {
            require(methods)
            ntheta <- 2
            theta.full <- (1:ntheta)/3.217233456
            G1 <- inla.barrier.q.plus(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G1[G1 != 0] <- 1
            theta.full <- (1:ntheta)^2/12.1543534
            G2 <- inla.barrier.q.plus(fem = fem, ranges = exp(theta.full[2]) * 
                c(1, range.fraction), sigma = exp(theta.full[1]))
            G2[G2 != 0] <- 1
            return(G1 + G2)
        }
        mu <- function(theta) numeric(0)
        log.norm.const <- function(theta) numeric(0)
        quit <- function(theta) invisible()
        val <- do.call(match.arg(cmd), args = list(theta))
        return(val)
    }
#   barrier.triangles <- unique(barrier.triangles)
    obj <- list()
    obj$prior.sigma <- prior.sigma
    obj$prior.range <- prior.range
    obj$range.fraction <- range.fraction
    obj$inla.barrier.q <- inla.barrier.q.plus
    obj$fem <- inla.barrier.fem.plus(mesh, barrier.triangles = barrier.triangles)
    barrier.model <- inla.rgeneric.define(model = barrier.rgeneric.model, 
        optimize = TRUE, obj = obj)
    if (!is.na(prior.sigma[2]) && !is.na(prior.range[2])) {
    }
    else {
        warning("Not properly tested, let us know if you have problems.")
    }
    return(barrier.model)
}
```

```{r}
inla.barrier.pcmatern(mesh, triBarrier)
inla.barrier.pcmatern.plus(mesh, list(triBarrier1,triBarrier2))
```


SOME CODE EXAMPLES IN:
*https://haakonbakkagit.github.io/btopic103.html*
*SPDE book: pg 177*

```{r}
inla.barrier.pcmatern()
##EXAMPLE
barrier.model = inla.barrier.pcmatern(mesh, barrier.triangles = barrier, prior.range = c(1.44, 0.5), prior.sigma = c(0.7, 0.5), range.fraction = 0.1)

inla.rgeneric.q
inla.barrier.polygon
##EXAMPLE
range = 3
# - the spatial range parameter
Q = inla.rgeneric.q(barrier.model, "Q", theta = c(0, log(range)))
```
*https://haakonbakkagit.github.io/btopic103.html*
*SPDE book: pg 177*
