Different Geometries.

Using functions from diff_transparencyEx1fx.Rmd file
I'm not running functions again so run that script first.

Start with fx.pre.field to define polygons and construct the mesh.

width = c(1.5, 1.5)

```{r}
pre.field1 <- fx.pre.field(width = c(1.5, 1.5), loc.data = TRUE)

pf <- pre.field1
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
range.fraction <- c(0.1, 0.1)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot(pf$poly.original, main="Barrier area polygon")
ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =pf$loc.data_sf,
          col='purple',size=1.7,alpha=0.5) 

plot.transparency(nfrac = 2,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1)
```


```{r}
pre.field2 <- fx.pre.field(width = c(1.5, 1.5), loc.data = TRUE,
                           set.inla.seed = 8)
pf <- pre.field2

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =pf$loc.data_sf,
          col='purple',size=1.7,alpha=0.5)
```


```{r}
pre.field3 <- fx.pre.field(width = c(1.5, 1.5), loc.data = TRUE,
                           set.inla.seed = 3)
pf <- pre.field3

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =pf$loc.data_sf,
          col='purple',size=1.7,alpha=0.5)

mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
range.fraction <- c(0.1, 0.1)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 2,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  set.inla.seed = 3)
```

```{r}
pre.field4 <- fx.pre.field(width = c(1.5, 1.5), loc.data = TRUE,
                           n = 20)
pf <- pre.field4

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =pf$loc.data_sf,
          col='purple',size=1.7,alpha=0.5)

mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
range.fraction <- c(0.1, 0.1)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 2,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1)
```

seed = 8 and seed = 3.
width = c(0.4, 0.4)
n of sample in fx.pre.field = 20
nfrac = 10
start at 0.1

see path to get the folder where the gif s

```{r}
pre.field5 <- fx.pre.field(loc.data = T,
                          set.inla.seed = 8,
                          n = 20)

pf <- pre.field5
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 10,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  set.inla.seed = 8,
                  gif.path = "gif/gif.fx/width=c(0.4,0.4) dif_trans1fx/nfrac = 10, n=20/seed8/",
                  plot.points = 
                    points(loc.data, pch = 16, cex = 0.5, 
                           col=alpha('black', 0.5)))

pre.field6 <- fx.pre.field(loc.data = T,
                          set.inla.seed = 3,
                          n = 20)

pf <- pre.field6
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 10,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  set.inla.seed = 3,
                  gif.path = "gif/gif.fx/width=c(0.4,0.4) dif_trans1fx/nfrac = 10, n=20/seed3/",
                  plot.points = 
                    points(loc.data, pch = 16, cex = 0.5, 
                           col=alpha('black', 0.5)))
```

width = c(2, 2)
n of sample in fx.pre.field = 20 and 10
left.poly = 0.01
nfrac = 5
max.frac = 100

see path to get the folder where the gif are

```{r}
pre.field7 <- fx.pre.field(loc.data = T,
                           width = c(2, 2),
                          n = 20)

pf <- pre.field7
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2,2) plots/n=20/")
##
pre.field8 <- fx.pre.field(loc.data = T,
                           width = c(2, 2),
                          n = 10)

pf <- pre.field8
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2,2) plots/n=10/")
plot(poly.bar.orginal)

##
pre.field7.1 <- fx.pre.field(loc.data = T,
                           width = c(2, 2),
                           smalldist = 0.8,
                          n = 20)

pf <- pre.field7.1
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2,2) plots/n=20/smdist=0.8/")

##
pre.field7.2 <- fx.pre.field(loc.data = T,
                           width = c(2, 2),
                           smalldist = 0.3,
                          n = 20)

pf <- pre.field7.2
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2,2) plots/n=20/smdist=0.3/")
plot(poly.bar.orginal)
```


```{r}
pre.field9 <- fx.pre.field(loc.data = T,
                           width = c(2.5, 2.5),
                           smalldist = 0.8,
                           n = 20)

pf <- pre.field9
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  max.frac = 100,
                  left.poly = 0.01,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2.5,2.5) plots/smdist=0.8/")
##
pre.field9.1 <- fx.pre.field(loc.data = T,
                           width = c(2.5, 2.5),
                           smalldist = 1,
                           n = 20)
                    

pf <- pre.field9.1
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  max.frac = 100,
                  left.poly = 0.01,
                  poly.bar.orginal = poly.bar.orginal, 
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(2.5,2.5) plots/smdist=1/")
```


```{r}
pre.field10 <- fx.pre.field(loc.data = T,
                           width = c(0.5, 3),
                           smalldist = 0.5,
                           n = 20)
pf <- pre.field10
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  max.frac = 100,
                  left.poly = 0.01,
                  poly.bar.orginal = poly.bar.orginal, 
                  range = 10,
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(0.5,3) plots/")

```

```{r}
pre.field10.1 <- fx.pre.field(loc.data = T,
                           width = c(0.3, 3),
                           smalldist = 0.5,
                           n = 30)
pf <- pre.field10.1
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal

plot.transparency(nfrac = 5,
                  max.frac = 100,
                  left.poly = 0.01,
                  poly.bar.orginal = poly.bar.orginal, 
                  range = 10,
                  fps = 1,
                  gif.path = "gif/gif.fx/width=c(0.3,3) plots/")

```


























