# TUTORIAL: Polygons and Coastlines
https://haakonbakkagit.github.io/btopic127.html

```{r}
library(INLA)
library(rgdal)
library(rgeos)
library(ggmap)
set.seed(2018)
```

```{r}
# First polygon
pl1 <- Polygon(cbind(c(0,15,15,0,0), c(5,0,20,20,5)), hole=FALSE)
# Hole in the first polygon
h1 <- Polygon(cbind(c(5,12,10,5,5), c(7,7,15,15,7)), hole=TRUE)
# Second polygon
pl2 <- Polygon(cbind(c(15,20,20,30,30,15,15), c(10,10,0,0,20,20,10)), hole=FALSE)

sp <- SpatialPolygons(list(Polygons(list(pl1, h1), '0'), Polygons(list(pl2), '1')))

SpatialPolygons(list(Polygons(list(pl2), '1')))

plot(sp, main = 'Polygon')
?dplyr::select

plot(cbind(c(5,12,10,5,5), c(7,7,15,15,7)))

```

In R, the "@" symbol is used to access slots or components of an object that has a class defined with the S4 class system. This is often used with objects from spatial data packages like sp and sf. The "@" symbol is used to access internal components of an object, which are typically stored in slots.


```{r}
# You can run this code chunk
pl1 <- Polygon(cbind(c(22.80, 22.80, 26.85, 26.85, 22.80), 
                     c(38.06, 34.88, 34.88, 38.06, 38.06)), hole=FALSE)

sp <- SpatialPolygons(list(Polygons(list(pl1), '0')), 
                      proj4string =CRS("+proj=longlat +datum=WGS84"))
plot(sp)
```


```{r}
# create a polygon representing the area of interest
pll = Polygon(sp@polygons[[1]]@Polygons[[1]]@coords, hole = F)
sp@polygons[[1]]@Polygons
length(sp@polygons[[1]]@Polygons)
class(pll)
length(sp@polygons[[1]]@Polygons)

# https://github.com/haakonbakkagit/haakonbakkagit.github.io/tree/master/data/btopic127
shape5 <- rgdal::readOGR(dsn = "data/", layer = "shape5")

# number of polygons representing the islands
n_poly = length(shape5@polygons[[1]]@Polygons)
idx = seq(1:n_poly)

# create a list of holes
hole_list = lapply(idx, function(n) Polygon(shape5@polygons[[1]]@Polygons[[n]]@coords, hole = T)) 

# create the final Spatial Polygons
new_sp = SpatialPolygons(list(Polygons(append(hole_list, pll),'1')))
# take a look
plot(new_sp)
mesh_poly = inla.mesh.2d(boundary = new_sp, max.edge = 0.2)
plot(mesh_poly, main = '')

# same without perimeter
# create the final Spatial Polygons
new_sp = SpatialPolygons(list(Polygons(hole_list,'1')))
# take a look
plot(new_sp)
mesh_poly = inla.mesh.2d(boundary = new_sp, max.edge = 0.2)
plot(mesh_poly, main = '')
str(new_sp)
```


```{r}
?as
```





Paula has a tutorial:
TUTORIAL: terra pckge Paula https://www.paulamoraga.com/tutorial-terra/






























